---
title: "Aging Decision & Memory Study Preliminary Analysis"
output: html_notebook
author: Megan McMahon
---

Aging Decision & Memory Study
Correlation Analysis

```{r setup, echo = FALSE}
MAIN_DIR <- "~/Box/ADM_Study/ADM"
ACT_DIR <- "~/Box/ADM_Study/ADM/CAR_analysis/cleaned_09-21-2018"
IN_DIR <- "~/Box/ADM_Study/ADM/CAR_analysis/cleaned_09-21-2018/new" 
PROC_DIR <- "~/Box/ADM_Study/ADM/CAR_analysis/cleaned_09-21-2018/processed"
RESID_DIR <- "~/Box/ADM_Study/ADM/CAR_analysis/cleaned_09-21-2018/residuals"
CAR_DIR <- "~/Box/ADM_Study/ADM/CAR_Analysis"
FIGURE_DIR <- "~/Box/ADM_Study/ADM/Figures"

library(lubridate)
library(ggplot2) 
library(dplyr)
library(stringr)
```

# Prep for nparACT 
## Convert to .txt

## Before getting started
Check csv output from the actigraph.py script. Ensure naming is consistent for each of the files (should start with record ID number, not "ADM_")

## 1) Convert actigraph files to .txt
This is important because when we input the actigraph data into the nparACT package later on, it will only accept .txt files.

For more information about the format of input files to run the nparACT package, see https://cran.r-project.org/web/packages/nparACT/nparACT.pdf. 

```{r convert to txt}

# create new directory
NEW_DIR <- paste0(ACT_DIR, "/text_10day")
if (!dir.exists(NEW_DIR)) {
  dir.create(NEW_DIR)
} else {
  print("new directory already exists")
}

#Gets files and list of 4 digit subject IDs
setwd(IN_DIR)
files <- list.files(IN_DIR, pattern= "New_Analysis.csv", full.names = TRUE)
record_id <- substr(basename(files),1, 5)

# Get list of duplicated files
SPLIT <- strsplit(files, "/")
dup_files = files[duplicated(substr(sapply(SPLIT, "[", 10), 0, 5))]

file_base <- paste0(record_id, ".txt")


# Read in .csv files, set new wd and save .txt to new directory, reset directory
 act_old = data.frame()
 for (i in 1:length(files)) {
   #setwd(IN_DIR)
   filename <- paste0(NEW_DIR,"/", record_id[i],".txt")
   act <- read.csv(files[i], skip = 1, header = TRUE, row.names = NULL)
   act [,1] <- substr(ymd_hms(act[,1], tz = NULL), 0, str_length(ymd_hms(act[,1], tz = NULL)-4))
   colnames(act) <- c("datetime", "activity")
   paste0(record_id[i], " wore actigraph for ", round(difftime(max(act$datetime), min(act$datetime))), " days")
   #only keeping most recent 10 days of data for all subjects
   start = ymd_hms(max(act$datetime), tz=NULL) - days(10)
   act <- act[act$datetime >= start,]
   #setwd(NEW_DIR)
   outfiles <- list.files(NEW_DIR)
   write.table(act, file = filename, col.names = FALSE, row.names = FALSE, sep = " ")
 }
```

## CAR processed
### 1) Convert Variables
This converts actigraphy measures to formats which will be input into the circadian activity script.
#### Note: this takes a LONG time

```{r CAR process}
library(stats)
#library(readr)
#library(reshape2)

files=list.files(IN_DIR, pattern= "*New_Analysis.csv", full.names = TRUE)
SPLIT <- strsplit(files, "/")
dup_files = files[duplicated(substr(sapply(SPLIT, "[", 10), 0, 5))]

for (i in 1:length(files)){
  d=read.csv(files[i],header=TRUE,sep=",",na.string=" ")
  #d$Time <- strftime(as.character(d[,1]), "%Y-%m-%d %H:%M:%S")
     #only keeping most recent 10 days of data for all subjects
  start = ymd_hms(max(as.character(d$Time)), tz="UTC") - days(10)
  d$Time <- as.character(ymd_hms(d$Time), tz="UTC")
  d <- d[ymd_hms(d$Time) >= start,]
  d$Date <- strftime(d[,1], format = "%Y-%m-%d") 
  d$Time <- strftime(d[,1], format = "%H:%M:%S") 
  d$fixed_times=NULL
  d$report_times=NULL
  #converts factors into character and then time
  
  d_old <- data.frame()
  d$hour=hour(hms(d$Time))
  d$minute=minute(hms(d$Time))
  d$cloktime=d$hour+(d$minute/60)
  
  d$sub=substr(basename(files[i]),1, 5)
  subject=d$sub[1]
  filename <- paste0(PROC_DIR,"/", subject,"_fixed.csv")
  file_base <- paste0(subject, "_fixed.csv")
  outfiles <- list.files(PROC_DIR)
  
  #we want to overwrite (not concatenate) so this is commented out!
  
  # if (file_base %in% outfiles) {
  #   d <- rbind(d_old, d)
  #   print(paste0("Duplicate - appending new reading to existing processed csv file. Sub = ", subject))
  # }
  #d_old <- d
  write.csv(d,file=filename, row.names = FALSE)
}
```

## CAR residuals

```{r CAR residuals}

files = list.files(PROC_DIR, pattern = "*_fixed.csv", full.names = TRUE)

for (i in 1:length(files)){
  d=read.table(files[i],header=TRUE,sep=",",na.string="NA")
  subject = d$sub[1]
  name_resid=paste(RESID_DIR,subject,sep="/")
  d$twopio24 = (2*3.14159)/24 
  d$xcos = cos(d$twopio24*d$cloktime) 
  d$xsin = sin(d$twopio24*d$cloktime)
  
  #d$activity=as.character(d$ZCM)
  #d$activity=as.numeric(d$PIM, "NA")
  d$lactivity = log((d$Activity +1),10)
  
  allwatch=d[,c("sub","cloktime","lactivity","xcos","xsin","twopio24")]
  allwatch=na.omit(allwatch)
  
  model=lm(allwatch$lactivity ~ allwatch$xcos + allwatch$xsin)
  allwatch$linactxb=coef(model)['(Intercept)']
  allwatch$linactcos=coef(model)['allwatch$xcos']
  allwatch$linactsin=coef(model)['allwatch$xsin']
  #need column for residuals called linract
  allwatch$linract=model$residuals
  
  write.csv(allwatch,file=paste(name_resid,"_","residuals.csv",sep=""),row.names=FALSE)
} #end loop



removed = c()
results=data.frame(c())
r_files=list.files(RESID_DIR, pattern= "*_residuals.csv", full.names = TRUE)
i = 104
for (i in 1:length(r_files)){
  
  actres1=read.table(r_files[i],header=TRUE,sep=",")
  
  actres1$linactamp = sqrt(actres1$linactcos^2 + actres1$linactsin^2)
  actres1$linactmin = actres1$linactxb-actres1$linactamp 
  
  #using first row then adding columns for other rows
  if (sum(actres1$cloktime) == 0) {
    removed[i] <- print(r_files[i])
    next
  } else {
    for (p in 1:length(actres1$lactivity[1])){
      if (actres1$linactsin[1] > 0 & actres1$linactcos[1] > 0) {
        actres1$phase = atan(actres1$linactsin/actres1$linactcos)}
      else if (actres1$linactsin[1] > 0 & actres1$linactcos[1] < 0) {
        actres1$phase = 3.14159 - atan(actres1$linactsin/abs(actres1$linactcos))}
      else if (actres1$linactsin[1] < 0 & actres1$linactcos[1] < 0) {
        actres1$phase = 3.14159 + atan(abs(actres1$linactsin)/abs(actres1$linactcos))}
      else {(actres1$linactsin[1] < 0 & actres1$linactcos[1] > 0)
        actres1$phase = 2*3.14159 - atan(abs(actres1$linactsin)/(actres1$linactcos))} 
    }
  }
  
  write(removed, file = paste0(MAIN_DIR,"/CAR_analysis/cleaned_09-21-2018/removed/removed.txt"))
  actres1$linactacro = actres1$phase*24/(2*3.14159) 
  
  #get sum of squares (uss variable)
  linractuss=(sum((actres1$linract)^2))-((sum(actres1$linract))^2/(length(actres1$linract))) 
  
  #num_nonmissingvalues
  nlinract=dim(actres1)[1]
  
  
  #nonlinear regression
  carhythm = function(actphi,actbeta,actalph,actmin,actamp,cloktime) {
    twopio24 = (2*3.14159)/24 
    rhythm = cos(twopio24*(cloktime - actphi ))
    lexpt=actbeta*(rhythm - actalph)
    expt = exp(lexpt)
    er = expt/(1 + expt)
    actmin + actamp*er
    
  }

  
  #if want it to print out iterations change trace=TRUE
  b=nls(actres1$lactivity ~carhythm(actphi,actbeta,actalph,actmin,actamp,cloktime),
        data=actres1, algorithm="port",
        start=list(actphi = 12,actbeta = 2.00,actalph = 0.0,actmin =0,actamp=1),
        lower=list(actphi = -3,actbeta = 0,actalph = -1,actmin =0,actamp=1),
        upper=list(actphi = 27,actbeta = Inf,actalph = 1,actmin =Inf,actamp=5),
        control=list(maxiter=200, warnOnly=TRUE),
        trace=FALSE)

  actres1$rnlact=resid(b)
  actres1$pnlact=fitted(b)	
  
  
  # take estimates from model and add to actres (in SAS all5) changes parameter names
  ## x beginning variables are the same as the e beginning variables
  actres1$xactphi=coef(b)['actphi']
  actres1$xactbeta=coef(b)['actbeta']
  actres1$xactalph=coef(b)['actalph']
  actres1$xactmin=coef(b)['actmin']
  actres1$xactamp=coef(b)['actamp']
  
  actres1$coact = actres1$linactxb + actres1$linactcos*actres1$xcos + actres1$linactsin*actres1$xsin

  ncssrnlact=(sum((actres1$rnlact)^2))-((sum(actres1$rnlact))^2/(length(actres1$rnlact)))
  cssact=(sum((actres1$lactivity)^2))-((sum(actres1$lactivity))^2/(length(actres1$lactivity)))
  nact=length(actres1$lactivity)
  nlinract=length(actres1$lactivity) 
  
  
  actacos=acos(actres1$xactalph[1])/actres1$twopio24[1]
  acthalftimel=-actacos + actres1$xactphi[1]
  acthalftimer=actacos + actres1$xactphi[1]
  actwidthratio = 2*actacos/24
  
  
  if(actres1$xactalph[1] < -0.99 |actres1$xactalph[1] > 0.99){
    actwidthratio = 0.5
    acthalftimel = (actres1$xactphi[1] - 6)
    acthalftimer = actres1$xactphi[1] + 6
  }
  
  actdervl = -sin((acthalftimel - actres1$xactphi[1])*actres1$twopio24[1])
  actdervr = -sin((acthalftimer - actres1$xactphi[1])*actres1$twopio24[1])	
  
  #sd is standard error I can get that from nls output 
  sdactphi=summary(b)$coefficients['actphi',2]
  sdactbeta=summary(b)$coefficients['actbeta',2]
  sdactalph=summary(b)$coefficients['actalph',2]
  sdactmin=summary(b)$coefficients['actmin',2]
  sdactamp=summary(b)$coefficients['actamp',2]
  
  #t is t value from model
  tactphi=summary(b)$coefficients['actphi',3]
  tactbeta=summary(b)$coefficients['actbeta',3]
  tactalph=summary(b)$coefficients['actalph',3]
  tactmin=summary(b)$coefficients['actmin',3]
  tactamp=summary(b)$coefficients['actamp',3]
  
  rsqact = (cssact - ncssrnlact)/cssact  
  fact = ((cssact - ncssrnlact)/4)/(ncssrnlact/(nlinract - 5))
  ndf = 4
  ddfact = nlinract - 5
  efact = ddfact/(ddfact - 2)
  varfact = ( 2/ndf )*( efact**2 )*( (ndf + ddfact -2)/(ddfact - 4) )  #wilks p. 187 */;
  tfact = (fact - efact)/sqrt(varfact)
  varact = cssact/(nlinract - 1)
  mselinact = linractuss/(nlinract - 3)
  msenlinact = (ncssrnlact/(nlinract - 5))
  fnlrgact = ((linractuss - ncssrnlact)/2)/(ncssrnlact/(nlinract - 5)) 
  flinact = ((cssact - linractuss)/2)/(linractuss/(nlinract - 3)) 
  
  actmesor = actres1$xactmin[1] + (actres1$xactamp[1]/2) 
  actupmesor = acthalftimel
  actdownmesor = acthalftimer 
  actamp=actres1$xactamp[1]
  actbeta=actres1$xactbeta[1]
  actphi=actres1$xactphi[1]
  actmin=actres1$xactmin[1]
  actalph=actres1$xactalph[1]
  subject=actres1$sub[1]
  session=actres1$session[1]
  #rhythm=c(subject,actamp,actbeta,actphi,actmin,actmesor,actupmesor,actdownmesor,actalph,actwidthratio,rsqact,fact,fnlrgact)
  rhythm=c(as.character(subject), actamp,actbeta,actphi,actmin,actmesor,actupmesor,actdownmesor,actalph,actwidthratio,rsqact,fact,fnlrgact)
  newline <- data.frame(t(rhythm))
  results <- rbind(results, newline)
  
}


colnames(results)=c("subject","actamp","actbeta","actphi","actmin","actmesor","actupmesor","actdownmesor","actalph","actwidthratio","rsqact","fact","fnlrgact")
write.csv(results, file=(paste0(MAIN_DIR, "/data/circadian_rhythms", format(Sys.time(), "%Y-%m-%d"), ".csv")),row.names=FALSE)


```

## nparACT
3) Run nparACT package to compute IS, IV, RA, L5, M10, L5 time, M10 time

Computes interdaily stability (IS), intradaily variability (IV) & the relative amplitude
(RA) from actigraphy data as described in Blume et al. (2016). Additionally, it also computes L5 (i.e. the 5 hours with lowest average actigraphy amplitude) and M10 (the 10 hours with highest average amplitude) as well as the respective start times. 

The flex versions will also compute the L-value for a user-defined number of minutes. IS describes the strength of coupling of a rhythm to supposedly stable zeitgebers.

It varies between 0 (Gaussian Noise) and 1 for perfect IS. IV describes the fragmentation of a rhythm, i.e. the frequency and extent of transitions between rest and activity.

It is near 0 for a perfect sine wave, about 2 for Gaussian noise and may be even higher when a definite ultradian period of about 2 hrs is present. RA is the relative amplitude of a rhythm. Note that to obtain reliable results, actigraphy data should cover a reasonable number of days.

```{r}
library(nparACT)
library(dplyr)
library(stringr)


files <- list.files(IN_DIR, pattern= "New_Analysis.csv", full.names = TRUE)
record_id <- substr(basename(files),1, 5)

#Get IS, IV, RA, L5, and M10 values
npar_data <- nparACT_base_loop(NEW_DIR,SR = 2/60)
record_id <- unique(record_id)
base_data <- cbind(npar_data, record_id)
base_data <- base_data[c("record_id","IS", "IV", "RA", "L5", "L5_starttime", "M10", "M10_starttime")]

# Convert Start Time Variables
base_data$L5_start_diff <-  base_data$L5_starttime  
base_data$M10_start_diff <-  base_data$M10_starttime  
base_data <- transform(base_data, M10_start_diff = as.difftime(M10_start_diff, units = "hours"), 
               L5_start_diff = as.difftime(L5_start_diff, units = "hours"))

save(base_data, file = paste0(MAIN_DIR, "/data/nparact.RData"))
```

## Merge data
4) Merge Data


```{r}
library(dplyr)
library(stringr)

# Import Redcap Data

setwd(MAIN_DIR)
redcap <- read.csv(paste0(MAIN_DIR,"/data/AgingDecMem_DATA_2018-09-20_1532.csv"))
#redcapday2 <- read.csv(paste0(MAIN_DIR,"/data/AgingDecMem_DATA_2018-10-12_0817.csv"))


files <- list.dirs("~/Box/ADM_Study/ADM/data/Behavioral", full.names = FALSE)
record_id <- substr(basename(files),1, 5)

###Assign Age Groups
redcap <- redcap[!is.na(redcap$age),]
redcap$group[ redcap$age >=18 & redcap$age <=30 ] <- "YA"
redcap$group[ redcap$age >=60 & redcap$age <=90 ] <- "OA"
redcap <- redcap[!is.na(redcap$group),]

redcap <- subset(redcap, redcap$redcap_event_name == "online_eligibility_arm_1")
#redcap <- subset(redcap,!duplicated(redcap$record_id)) Not doing anything


#Assign subject numbers
redcap$record_id <- str_pad(redcap$record_id, 4, pad = "0")
for (i in 1:length(redcap$record_id)) {
  if (redcap$group[i] == "OA") {
    redcap$record_id[i] <- paste0("4", redcap$record_id[i])
  } else if (redcap$group[i] == "YA") {
    redcap$record_id[i] <- paste0("3", redcap$record_id[i])
  }
}

save(redcap, file = paste0(MAIN_DIR,"/data/redcap.RData"))

#Load CAR analysis
c=read.csv("~/Box/ADM_Study/ADM/data/circadian_rhythms2018-10-31.csv")

#Merge CAR and nparact
sleep_data <- merge(base_data, c, by.x = "record_id", by.y = "subject") 
sleep_data$record_id <- as.character(sleep_data$record_id)
psqi<- data.frame(redcap$record_id, redcap$global_psqi)
colnames(psqi) <- c("record_id", "global_psqi")

save(sleep_data, file = paste0(MAIN_DIR,"/data/sleepdata.RData"))

#Merge actigraph data and redcap data
all_data <- merge(sleep_data, redcap, by = "record_id")
all_data$global_psqi[all_data$global_psqi > 21] <- NA

memmatch <- read.csv("~/Box/ADM_Study/ADM/data/memmatch_results.csv")

d <- merge(all_data, memmatch, by.x = "record_id", by.y = "subnum")

save(d, file = paste0(MAIN_DIR,"/data/merged_data.RData"))
```
