---
title: "Age Differences in Functional Connectivity Metrics"
author: "Megan McMahon"
date: "1/13/2020"
output: html_document
---

# Contents
* [Differences in functional connectivity measures across age groups]
* [Rest-activity measures and cognition]
* [*1]
* [Network measures and cognition]
* [*2]
* [Rest-activity measures and functional connectivity networks]
* [Nodewise Participation Coefficient]

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(reshape2)
library(corrplot)
#library(beset)

load("~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2019-12-25.RData")

cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# load("~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2019-12-13.RData")
# bct <- read_csv('~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/rest/bct/bct_x.csv')
# d <- merge(d, bct, by = "record_id", all = TRUE)
# d$actquot <- d$actamp/d$actmesor
# d$Group <- factor(ifelse(d$record_id < 40000, 0, 1), labels = c("Young Adults", "Older Adults"))

# mem <- read_csv("~/Box/CogNeuroLab/Aging Decision Making R01/Data/memmatch_results.csv")
# mem$X1 <- NULL
# 
# mem %>%
#   group_by(record_id, cond) %>%
#   summarise_each(funs(mean(., na.rm = TRUE)), isCorrect) %>%
#   spread(cond, isCorrect) -> acc
# 
# colnames(acc) <- paste0("acc_cond_", colnames(acc))
# 
# mem %>%
#   group_by(record_id, cond) %>%
#   summarise_each(funs(mean(., na.rm = TRUE)), RT_c) %>%
#   spread(cond, RT_c) -> rt
# 
# colnames(rt) <- paste0("rt_cond_", colnames(rt))
# 
# d <- merge(d, acc, by.x = "record_id", by.y = "acc_cond_record_id")
# d <- merge(d, rt, by.x = "record_id", by.y = "rt_cond_record_id")
# save(d, file = "~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2019-12-25.RData")
#
# rpx <- read_csv("~/Box/CogNeuroLab/Aging Decision Making R01/Data/Actigraphy/Combined Export File.csv")
# 
# rpx %>%
#   filter(interval_type == "Sleep Summary", interval_number == "Average(n)") %>%
#   select(-data_start_date, -data_start_time, -start_date, -start_time, -end_date, -end_time) -> rpx_mean
# 
# head(rpx_mean)
# 
# d <- merge(d, select(rpx_mean, subject_id, sleep_time, total_ac, onset_latency, efficiency), by.x = "record_id", by.y = "subject_id", all = TRUE)
# d$sleep_efficiency <- d$efficiency
# d$efficiency <- NULL
# 
# save(d, file = "~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2020-01-13.RData")

ya_data <- d[d$Group == "Young Adults",]
oa_data <- d[d$Group == "Older Adults",]

```

# PsychFest Graphs
```{r}


d %>%
  ggplot(aes(fill = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = IS)) + 
  theme_minimal() + 
  scale_fill_brewer(palette="Set1") + 
  xlab(element_blank()) + ylab("Interdaily Stability") +
  theme(legend.position="none", text = element_text(size=20))
  ggsave('~/Box/PsychFest/IS-group.png', dpi = 300)

dd %>%
  ggplot(aes(fill = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = actamp)) + 
  theme_minimal() + 
  scale_fill_brewer(palette="Set1") + 
  xlab(element_blank()) + ylab("Amplitude") +
  theme(legend.position="none", text = element_text(size=20)) +
  ggsave('~/Box/PsychFest/amp-group.png', dpi = 300)

dd %>%
  ggplot(aes(fill = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = actphi)) + 
  theme_minimal() + 
  scale_fill_brewer(palette="Set1") + 
  xlab(element_blank()) + ylab("Acrophase") +
  theme(legend.position="none", text = element_text(size=20)) +
  ggsave('~/Box/PsychFest/phi-group.png', dpi = 300)

t.test(actalph ~ Group, data = d) # 0.02
t.test(actbeta ~ Group, data = d) # 0.04495
t.test(actphi ~ Group, data = d) # <<<<
t.test(IS ~ Group, data = d) # <<<
d$actquot <- d$actamp / d$actmesor
t.test(actquot ~ Group, data = d) # 0.03


###

summary(lm(dmn_participation_x ~ actamp*Group, data = dd))

lm1 <- lm(dmn_participation_x ~ actamp, data = d[d$Group == 'Older Adults',])
lm2 <- lm(dmn_participation_x ~ actamp2 + actamp, data = d[d$Group == 'Older Adults',])
lm3 <- lm(dmn_participation_x ~ actamp3 + actamp2 + actamp, data = d[d$Group == 'Older Adults',])

AIC(lm1)
AIC(lm2)
AIC(lm3) # best

d %>%
  filter(actamp < 2.5) %>%
  ggplot() + 
  geom_point(aes(x = actquot, y = dmn_participation_x, group = Group, color = Group)) + 
  stat_smooth(aes(x = actquot, y = dmn_participation_x, group = Group, color = Group), method = 'lm', se = FALSE) + 
  theme_minimal() + 
  scale_color_brewer(palette="Set1") + 
  theme(legend.position="none", text = element_text(size=20)) +
  facet_wrap(. ~ Group) +
  xlab('Amplitude') + ylab('DMN Participation') +
  ggsave('~/Box/PsychFest/amp_dmn_participation_2.png', dpi = 300)


d <- dd


d$actamp2 = d$actamp^2
d$actamp3 = d$actamp^3
d$actamp4 = d$actamp^4

summary(lm(fpn_participation_x ~ age, data = d[d$Group == 'Young Adults',])) #NS
summary(lm(fpn_participation_x ~ age, data = d[d$Group == 'Older Adults',])) #NS

lm1 <- lm(fpn_participation_x ~ actamp, data = d[d$Group == 'Young Adults',])
lm2 <- lm(fpn_participation_x ~ actamp2 + actamp, data = d[d$Group == 'Young Adults',])
lm3 <- lm(fpn_participation_x ~ actamp3 + actamp2 + actamp, data = d[d$Group == 'Young Adults',])
lm4 <- lm(fpn_participation_x ~ actamp4 + actamp3 + actamp2 + actamp, data = d[d$Group == 'Young Adults',])

AIC(lm1)
AIC(lm2)
AIC(lm3) #best, NS
AIC(lm4)

summary(lm2) #NS 

lm1 <- lm(fpn_participation_x ~ actamp, data = d[d$Group == 'Older Adults',])
lm2 <- lm(fpn_participation_x ~ actamp2 + actamp, data = d[d$Group == 'Older Adults',])
lm3 <- lm(fpn_participation_x ~ actamp3 + actamp2 + actamp, data = d[d$Group == 'Older Adults',])
lm4 <- lm(fpn_participation_x ~ actamp4 + actamp3 + actamp2 + actamp, data = d[d$Group == 'Older Adults',])

AIC(lm1)
AIC(lm2)
AIC(lm3) # best
AIC(lm4)

summary(lm4)

d %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = fpn_participation_x, group = Group, color = Group)) + 
  stat_smooth(data = subset(d, Group == 'Older Adults'), aes(x = actamp, y = fpn_participation_x, group = Group, color = Group), formula = y ~ poly(x, 3), method = 'lm', se = FALSE) + 
  theme_minimal() + 
  scale_color_brewer(palette="Set1") + 
  theme(legend.position="none", text = element_text(size=20)) +
  facet_wrap(. ~ Group, scales = 'free_y') +
  xlab('Amplitude') + ylab('FPN Participation') 
  ggsave('~/Box/PsychFest/amp_fpn_participation.png', dpi = 300)

summary(lm(dmn_participation_x ~ age, data = d[d$Group == 'Young Adults',])) #NS
summary(lm(dmn_participation_x ~ age, data = d[d$Group == 'Older Adults',])) #NS
###

lm1 <- lm(dmn_participation_x ~ actamp, data = d[d$Group == 'Young Adults',])
lm2 <- lm(dmn_participation_x ~ actamp2 + actamp, data = d[d$Group == 'Young Adults',])
lm3 <- lm(dmn_participation_x ~ actamp3 + actamp2 + actamp, data = d[d$Group == 'Young Adults',])
lm4 <- lm(dmn_participation_x ~ actamp4 + actamp3 + actamp2 + actamp, data = d[d$Group == 'Young Adults',])

AIC(lm1) #best
AIC(lm2)
AIC(lm3)
AIC(lm4)

summary(lm1) #

lm1 <- lm(dmn_participation_x ~ actamp, data = d[d$Group == 'Older Adults',])
lm2 <- lm(dmn_participation_x ~ actamp2 + actamp, data = d[d$Group == 'Older Adults',])
lm3 <- lm(dmn_participation_x ~ actamp3 + actamp2 + actamp, data = d[d$Group == 'Older Adults',])
lm4 <- lm(dmn_participation_x ~ actamp4 + actamp3 + actamp2 + actamp, data = d[d$Group == 'Older Adults',])

AIC(lm1)
AIC(lm2)
AIC(lm3) # best
AIC(lm4)

summary(lm3)

d %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = dmn_participation_x, group = Group, color = Group)) + 
  stat_smooth(data = subset(d, Group == 'Young Adults'), aes(x = actamp, y = dmn_participation_x, group = Group, color = Group), formula = y ~ poly(x, 1), method = 'lm', se = FALSE) + 
  stat_smooth(data = subset(d, Group == 'Older Adults'), aes(x = actamp, y = dmn_participation_x, group = Group, color = Group), formula = y ~ poly(x, 3), method = 'lm', se = FALSE) + 
  theme_minimal() + 
  scale_color_brewer(palette="Set1") + 
  theme(legend.position="none", text = element_text(size=20)) +
  facet_wrap(. ~ Group, scales = 'free_y') +
  xlab('Amplitude') + ylab('DMN Participation') +
  ggsave('~/Box/PsychFest/amp_dmn_participation.png', dpi = 300)

## np
np <- read_csv('~/Box/CogNeuroLab/Aging Decision Making R01/Data/Neuropsych/AgingDecMemNeuropsyc_DATA_2019-06-12_0708.csv')
d_np <- merge(d, np, by = 'record_id')
d_np <- filter(d_np, actamp < 3)

d_np$ef <- (d_np$ds_zscore + d_np$trails_b_z_score)/2

d_np %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = ef, group = Group, color = Group)) + 
  stat_smooth(data = d_np, aes(x = actamp, y = ef, group = Group, color = Group), formula = y ~ poly(x, 2), method = 'lm', se = FALSE) + 
  theme_minimal() + 
  scale_color_brewer(palette="Set1") + 
  theme(legend.position="none", text = element_text(size=20)) +
  facet_wrap(. ~ Group, scales = 'free_y') +
  xlab('Amplitude') + ylab('Executive Function')

summary(lm(ef ~ actamp*Group, d_np))
lm1 <- lm(ef ~ actamp, d_np)
lm2 <- lm(ef ~ actamp2 + actamp, d_np)
lm3 <- lm(ef ~ actamp3 + actamp2 + actamp, d_np)
lm4 <- lm(ef ~ actamp4 + actamp3 + actamp2 + actamp, d_np)


AIC(lm1)
AIC(lm2)
AIC(lm3)
AIC(lm4)

summary(lm2)

plot(lm2)

d_np %>%
  ggplot(aes(fill = Group, group = Group)) + 
  geom_boxplot(aes(x = EF_group, y = fact)) + 
  theme_minimal() + 
  scale_fill_brewer(palette="Set1") + 
  xlab(element_blank()) + ylab("Amplitude") +
  theme(legend.position="none", text = element_text(size=20))
```


# Differences in functional connectivity measures across age groups

```{r}
cr <- read_csv('~/Box/CogNeuroLab/Aging Decision Making R01/Data/graph_metrics.csv')


cr %>%
  select(Group, matches("wb_|dmn_|fpn_")) %>%
  na.omit() %>%
  melt(id.vars = "Group") -> d.melt

d.melt$network = rep(0, length(d.melt$network))
d.melt$network = ifelse(str_detect(d.melt$variable, "wb_"), "Whole Brain", d.melt$network)
d.melt$network = ifelse(str_detect(d.melt$variable, "dmn_"), "Default Mode Network", d.melt$network)
d.melt$network = ifelse(str_detect(d.melt$variable, "fpn_"), "Frontoparietal Network", d.melt$network)
d.melt$network

d.melt$variable <- str_to_title(sapply( str_split(d.melt$variable, "_", 3), "[", 2 ))
d.melt$Group <- factor(d.melt$Group, levels = c("Young Ad.meltults", "Old.melter Ad.meltults"))


d.melt %>%
  filter(network == 'Whole Brain') %>%
  filter(variable %in% c('Efficiency', 'modularity', 'Participation')) %>%
  ggplot(aes(fill = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = value)) + 
  facet_wrap( . ~ variable, scales = "free_y") +
  theme_minimal() + 
  scale_fill_brewer(palette="Set1") + 
  scale_x_d.meltiscrete(labels = c("YA", "OA")) + 
  xlab(element_blank()) + ylab(element_blank()) +
  theme(legend.position="bottom") +
  ggtitle("Whole Brain") +
  ggsave('~/Box/PsychFest/wb_boxplot.png', d.meltpi = 300)

d.melt %>%
  filter(network == 'Frontoparietal Network') %>%
  filter(variable %in% c('Efficiency', 'modularity', 'Participation')) %>%
  ggplot(aes(fill = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = value)) + 
  facet_wrap( . ~ variable, scales = "free_y") +
  theme_minimal() + 
  scale_fill_brewer(palette="Set1") + 
  scale_x_d.meltiscrete(labels = c("YA", "OA")) + 
  xlab(element_blank()) + ylab(element_blank()) +
  theme(legend.position="bottom") +
  ggtitle("Frontoparietal Network") +
  ggsave('~/Box/PsychFest/fpn_boxplot.png', d.meltpi = 300)

d.melt %>%
  filter(network == 'Default Mode Network') %>%
  filter(variable %in% c('Efficiency', 'modularity', 'Participation')) %>%
  ggplot(aes(fill = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = value)) + 
  facet_wrap( . ~ variable, scales = "free_y") +
  theme_minimal() + 
  scale_fill_brewer(palette="Set1") + 
  scale_x_d.meltiscrete(labels = c("YA", "OA")) + 
  xlab(element_blank()) + ylab(element_blank()) +
  theme(legend.position="bottom") +
  ggtitle("Default Mode Network") +
  ggsave('~/Box/PsychFest/d.meltmn_boxplot.png', d.meltpi = 300)

t <- t.test(wb_participation_x ~ Group, d.meltata = d.melt) ##
t
ggplot(d.melt, aes(x = Group, y = wb_participation_x, color = Group)) +
  geom_boxplot() + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red.melt")) +
  scale_x_d.meltiscrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Participation \n Coefficient") + 
  labs(caption = (paste("t = ", round.melt(t$statistic, 3), "p = ", round.melt(t$p.value, 3))))

t <- t.test(wb_efficiency_x ~ Group, d.meltata = d.melt) ##
t
ggplot(d.melt, aes(x = Group, y = wb_efficiency_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red.melt")) +
  scale_x_d.meltiscrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round.melt(t$statistic, 3), "p = ", round.melt(t$p.value, 3))))

t <- t.test(dmn_efficiency_x ~ Group, d.meltata = d.melt) ##
t
ggplot(d.melt, aes(x = Group, y = dmn_efficiency_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red.melt")) +
  scale_x_d.meltiscrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round.melt(t$statistic, 3), "p = ", round.melt(t$p.value, 3))))

t <- t.test(d.meltmn_modularity_x ~ Group, d.meltata = d.melt) ##
t
ggplot(d.melt, aes(x = Group, y = d.meltmn_modularity_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red.melt")) +
  scale_x_d.meltiscrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round.melt(t$statistic, 3), "p = ", round.melt(t$p.value, 3))))

t <- t.test(fpn_participation_x ~ Group, d.meltata = d.melt) ##
t
ggplot(d.melt, aes(x = Group, y = fpn_participation_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red.melt")) +
  scale_x_d.meltiscrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round.melt(t$statistic, 3), "p = ", round.melt(t$p.value, 3))))

t <- t.test(fpn_betweenness_x ~ Group, d.meltata = d.melt) ##
t
ggplot(d.melt, aes(x = Group, y = fpn_betweenness_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red.melt")) +
  scale_x_d.meltiscrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round.melt(t$statistic, 3), "p = ", round.melt(t$p.value, 3))))
```


```{r}

```

# Rest-activity measures and cognition

## Older Adults
```{r}
alpha = 0.05

oa_cor <- select(oa_data, age, IS:RA, actquot, actamp:fact, matches("zscore|z_score|time_trails"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```
```{r}
alpha = 0.05

oa_cor <- select(oa_data, age, sleep_time, onset_latency, sleep_efficiency, matches("zscore|z_score|time_trails"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```


```{r}
oa_data %>%
  select(age, IS, matches("zscore|z_score")) %>%
  melt(id.vars = "IS") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = IS, y = value)) +
  stat_smooth(aes(x = IS, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("IS and Neuropsych Measures")

oa_data %>%
  select(age, fact, matches("zscore|z_score")) %>%
  melt(id.vars = "fact") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = fact, y = value)) +
  stat_smooth(aes(x = fact, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("F-statistic and Neuropsych Measures")

oa_data %>%
  select(age, RA, matches("zscore|z_score")) %>%
  melt(id.vars = "RA") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = RA, y = value)) +
  stat_smooth(aes(x = RA, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("RA and Neuropsych Measures")

oa_data %>%
  select(age, IV, matches("zscore|z_score")) %>%
  melt(id.vars = "IV") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = IV, y = value)) +
  stat_smooth(aes(x = IV, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("IV and Neuropsych Measures")

oa_data %>%
  select(age, sleep_time, matches("zscore|z_score")) %>%
  melt(id.vars = "sleep_time") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = sleep_time, y = value)) +
  stat_smooth(aes(x = sleep_time, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("Sleep Time and Neuropsych Measures")

oa_data %>%
  select(age, sleep_efficiency, matches("zscore|z_score")) %>%
  melt(id.vars = "sleep_efficiency") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = sleep_efficiency, y = value)) +
  stat_smooth(aes(x = sleep_efficiency, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("Sleep Efficiency and Neuropsych Measures")
```

Trails B
```{r}
alpha = 0.05 

oa_cor <- select(oa_data, age, IS:RA, actquot, actamp:fact, sleep_time, sleep_efficiency, trails_b_z_score)
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```


```{r}
oa_data$TMT <- ifelse(oa_data$trails_b_z_score < median(oa_data$trails_b_z_score, na.rm = TRUE), "Low", "High")
ya_data$TMT <- ifelse(ya_data$trails_b_z_score < median(ya_data$trails_b_z_score, na.rm = TRUE), "Low", "High")
alpha = 0.05 

oa_data %>%
  na.omit(TMT) %>%
  select(age, IS:RA, actamp, actquot, fact, actalph, TMT) %>%
  melt(id.vars = "TMT") %>%
  ggplot() +
  theme_minimal() +
  geom_boxplot(aes(x = TMT, y = value)) +
  facet_wrap(. ~ variable, scales = "free_y") + 
  ggtitle("Rest-activity measures by TMT performance")
```

Out of curiosity from DTI...
```{r}
oa_data %>%
  select(age, actalph, matches("zscore|z_score|time_trails")) %>%
  melt(id.vars = "actalph") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = actalph, y = value)) +
  stat_smooth(aes(x = actalph, y = value), method = "lm") +
  facet_wrap(. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("actalph and Neuropsych Measures")
```

## Young Adults

```{r}
alpha = 0.05

ya_cor <- select(ya_data, age, IS:RA, actquot, actamp:fact, vc_zscore, ds_zscore, trails_a_z_score, trails_b_z_score)
ya_cor <- ya_cor[complete.cases(ya_cor), ]
ya_mat <- cor(ya_cor)
ya_res <- cor.mtest(ya_mat, conf.level = (1-alpha))
corrplot(ya_mat, p.mat = ya_res$p, sig.level = alpha, insig = "blank", type = "upper")
```

```{r}
alpha = 0.05

ya_cor <- select(ya_data, age, sleep_time, onset_latency, sleep_efficiency, vc_zscore, ds_zscore, trails_a_z_score, trails_b_z_score)
ya_cor <- ya_cor[complete.cases(ya_cor), ]
ya_mat <- cor(ya_cor)
ya_res <- cor.mtest(ya_mat, conf.level = (1-alpha))
corrplot(ya_mat, p.mat = ya_res$p, sig.level = alpha, insig = "blank", type = "upper")
```

## *1

```{r}
summary(lm(trails_b_z_score ~ sleep_efficiency, data = ya_data)) # p = 0.0468, B < 0 ? 
summary(lm(trails_b_z_score ~ Group*sleep_efficiency, data = d)) # *

summary(lm(trails_b_z_score ~ sleep_time, data = ya_data)) # p = 0.0472, B < 0 ? 
summary(lm(trails_b_z_score ~ Group*sleep_time, data = d)) # .
```

# Network measures and cognition

## Older Adults
```{r}
alpha = 0.05

oa_cor <- select(oa_data, age, matches("wb_|dmn_|fpn_"),matches("zscore|z_score"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```


```{r}
oa_data %>%
  select(age, dmn_participation_x, matches("zscore|z_score")) %>%
  melt(id.vars = "dmn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = dmn_participation_x, y = value)) +
  stat_smooth(aes(x = dmn_participation_x, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("DMN Participation and Neuropsych Measures")
```

```{r}
summary(lm(ds_zscore ~ dmn_participation_x, data = oa_data)) #NS
summary(lm(ds_zscore ~ Group*dmn_participation_x, data = d)) #NS
```


```{r}
oa_data %>%
  select(age, fpn_participation_x, matches("zscore|z_score")) %>%
  melt(id.vars = "fpn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = fpn_participation_x, y = value)) +
  stat_smooth(aes(x = fpn_participation_x, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("FPN Participation and Neuropsych Measures")
```

```{r}
summary(lm(trails_b_z_score ~ fpn_participation_x, data = oa_data)) # p = 0.0569

```


## Young Adults

```{r}
alpha = 0.05

ya_cor <- select(ya_data, age, matches("wb_|dmn_|fpn_"), vc_zscore, ds_zscore, trails_a_z_score, trails_b_z_score)
ya_cor <- ya_cor[complete.cases(ya_cor), ]
ya_mat <- cor(ya_cor)
ya_res <- cor.mtest(ya_mat, conf.level = (1-alpha))
corrplot(ya_mat, p.mat = ya_res$p, sig.level = alpha, insig = "blank", type = "upper")
```


```{r}
ya_data %>%
  select(age, fpn_participation_x, vc_zscore, ds_zscore, trails_a_z_score, trails_b_z_score) %>%
  melt(id.vars = "fpn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = fpn_participation_x, y = value)) +
  stat_smooth(aes(x = fpn_participation_x, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ylab("z-score") +
  ggtitle("FPN Participation and Neuropsych Measures")
```

## *2

```{r}
summary(lm(trails_b_z_score ~ fpn_participation_x, data = ya_data)) #NS
summary(lm(trails_b_z_score ~ Group*fpn_participation_x, data = d)) #p = 0.0161
```


# Rest-activity measures and functional connectivity networks

## Older Adults
```{r}
alpha = 0.05

oa_cor <- select(oa_data, age, IS:RA, actamp:fact, actquot, matches("wb_|dmn_|fpn_"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```

```{r}
oa_data %>%
  select(age, IS:RA, actamp, actalph, actupmesor, fact, fpn_participation_x) %>%
  melt(id.vars = "fpn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = value, y = fpn_participation_x)) +
  stat_smooth(aes(x = value, y = fpn_participation_x), method = "lm") +
  xlab("rest-activity measure") +
  facet_wrap (. ~ variable, scales = "free_x")
```

```{r}

d %>%
  select(record_id, Group, age, IS, matches('Efficiency|Modularity|Participation')) %>%
  melt(id.vars = c('Group', 'record_id', 'IS')) %>%
  ggplot() + 
  geom_point(aes(x = IS, y = value, group = Group, color = Group)) + 
  facet_wrap( . ~ variable, scales = "free_y") +
  theme_minimal() + 
  scale_color_brewer(palette="Set1") + 
  theme(legend.position="bottom") +
  ggtitle("Rest-Activity Stability and Network Metrics")
```

```{r}
d %>%
  ggplot() + 
  geom_point(aes(x = IS, y = dmn_participation_x, group = Group, color = Group)) + 
  stat_smooth(aes(x = IS, y = dmn_participation_x, group = Group, color = Group), method = 'lm') + 
  theme_minimal() + 
  scale_color_brewer(palette="Set1") + 
  theme(legend.position="bottom", text = element_text(size=20)) +
  xlab('Interdaily Stability') + ylab('DMN Participation') + 
  ggsave('~/Box/PsychFest/IS_dmn_participation.png', dpi = 300)
```

```{r}
summary(lm(wb_modularity_x ~ actamp*Group, data = d))
summary(lm(wb_modularity_x ~ actamp, data = d))
summary(lm(wb_modularity_x ~ IS*Group, data = d))
summary(lm(wb_modularity_x ~ IS, data = d))

summary(lm(dmn_participation_x ~ actamp*Group, data = d)) #####
summary(lm(dmn_participation_x ~ actamp*Group, data = d[d$actamp < 2.5,])) #####
summary(lm(dmn_participation_x ~ IS*Group, data = d)) #####

summary(lm(dmn_efficiency_x ~ actamp*Group, data = d))
summary(lm(dmn_efficiency_x ~ actamp, data = d))
summary(lm(dmn_efficiency_x ~ actamp*Group, data = d[d$actamp < 2.5,])) 
summary(lm(dmn_efficiency_x ~ actamp, data = d[d$actamp < 2.5,])) 
summary(lm(dmn_efficiency_x ~ IS*Group, data = d))
summary(lm(dmn_efficiency_x ~ IS, data = d))

summary(lm(fpn_participation_x ~ actamp*Group, data = d)) #####
summary(lm(fpn_participation_x ~ actamp*Group, data = d[d$actamp < 2.5,])) #####
summary(lm(fpn_participation_x ~ IS*Group, data = d))
summary(lm(fpn_participation_x ~ IS, data = d))

summary(lm(fpn_efficiency_x ~ actamp*Group, data = d))
summary(lm(fpn_efficiency_x ~ actamp*Group, data = d[d$actamp < 2.5,]))
summary(lm(fpn_efficiency_x ~ IS*Group, data = d))


```



```{r}
oa_data %>%
  select(age, IS:RA, actamp, actalph, actupmesor, fact, dmn_participation_x) %>%
  melt(id.vars = "dmn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = value, y = dmn_participation_x)) +
  stat_smooth(aes(x = value, y = dmn_participation_x), method = "lm") +
  xlab("rest-activity measure") +
  scale_color_manual(palette = 'Set1') +
  facet_wrap (. ~ variable, scales = "free_x")
```



## Young Adults
```{r}
ya_data %>%
  select(age, IS:RA, actamp, actalph, actupmesor, fact, fpn_participation_x) %>%
  melt(id.vars = "fpn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = value, y = fpn_participation_x)) +
  stat_smooth(aes(x = value, y = fpn_participation_x), method = "lm") +
  xlab("rest-activity measure") +
  facet_wrap (. ~ variable, scales = "free_x")
```

```{r}
ya_data %>%
  select(age, IS:RA, actamp, actalph, actupmesor, fact, dmn_participation_x) %>%
  melt(id.vars = "dmn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = value, y = dmn_participation_x)) +
  stat_smooth(aes(x = value, y = dmn_participation_x), method = "lm") +
  xlab("rest-activity measure") +
  facet_wrap (. ~ variable, scales = "free_x")
```

## Nodewise Participation Coefficient

[Blog Tutorial](https://drsimonj.svbtle.com/exploring-correlations-in-r-with-corrr)

[Missing values](http://bwlewis.github.io/covar/missing.html)

```{r}
library(corrr)

pcoef <- read_csv('~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/rest/bct/participation_nodewise_r.csv')

pcoef <- select(pcoef, record_id, matches("PFC"))
pcoef <- merge(pcoef, dplyr::select(d, record_id, vc_zscore, cvlt_ldelay_recall_zscore, cowat_zscore, ds_zscore, trails_b_z_score), by = 'record_id')
pcoef$ef_zscore <- (pcoef$trails_b_z_score + pcoef$ds_zscore )/2
pcoef$Group <- factor(ifelse(pcoef$record_id < 40000, 0, 1), labels = c("Young Adults", "Older Adults"))

oa_data <- filter(pcoef, record_id > 40000)
oa_data <- select(oa_data, -Group)

ya_data <- filter(pcoef, record_id < 40000)
ya_data <- select(ya_data, -Group, -cowat_zscore, -cvlt_ldelay_recall_zscore)

```

```{r}
focus_oa <- oa_data %>%
  na.omit() %>%
  correlate(method = "spearman", use = "complete.obs") %>%
  focus(vc_zscore, ds_zscore, trails_b_z_score, cvlt_ldelay_recall_zscore, cowat_zscore, ef_zscore)

focus_ya <- ya_data %>%
  correlate(method = "spearman", use = "complete.obs") %>%
  focus(vc_zscore, ds_zscore, trails_b_z_score, ef_zscore)

focus_oa.mlt <- melt(focus_oa, id.vars = 'rowname')
focus_ya.mlt <- melt(focus_ya, id.vars = 'rowname')
focus_cog <- merge(focus_ya.mlt, focus_oa.mlt, by = c("rowname", "variable"))

ggplot(data = na.omit(focus_oa.mlt[abs(focus_oa.mlt$value) > 0.35,]), aes(x = value, y = rowname)) + 
  geom_point(color = 'red') + 
  geom_point(data = drop_na(focus_ya.mlt[abs(focus_ya.mlt$value) > 0.35,]), color = 'blue') + 
  facet_grid( ~ variable,  scales='fixed') +
  ylab("node label") + xlab("r2 value")
```


```{r}
pcoef$PFC_mean <- rowMeans(select(pcoef, matches("PFC")))
pcoef %>%
  select(matches("PFC")) %>%
  select(matches("RH")) %>%
  rowMeans() -> pcoef$R_PFC_mean

pcoef %>%
  select(matches("PFC")) %>%
  select(matches("LH")) %>%
  rowMeans() -> pcoef$L_PFC_mean

sc_melt <- melt(select(pcoef, Group, R_PFC_mean, matches("zscore|z_score")) , id.vars = c("Group", "R_PFC_mean"))
sc_melt %>%
  ggplot(aes(color = Group, group = Group)) +
  geom_point(aes(x = R_PFC_mean, y = value, color = Group, group = Group)) + 
  stat_smooth(aes(x = R_PFC_mean, y = value, color = Group, group = Group), method = "lm") +
  scale_color_manual(values = c("blue", "red")) +
  ylab("z-score") +
  facet_wrap(. ~ variable) + ylim(-2,2)
```


```{r}
sc_melt <- melt(select(pcoef, Group, L_PFC_mean, matches("zscore|z_score")) , id.vars = c("Group", "L_PFC_mean"))
sc_melt %>%
  ggplot(aes(color = Group, group = Group)) +
  geom_point(aes(x = L_PFC_mean, y = value, color = Group, group = Group)) + 
  stat_smooth(aes(x = L_PFC_mean, y = value, color = Group, group = Group), method = "lm") +
  scale_color_manual(values = c("blue", "red")) +
  ylab("z-score") +
  facet_wrap(. ~ variable) + ylim(-2,2)
```

```{r}
sc_melt <- melt(select(pcoef, Group, PFC_mean, matches("zscore|z_score")) , id.vars = c("Group", "PFC_mean"))
sc_melt %>%
  ggplot(aes(color = Group, group = Group)) +
  geom_point(aes(x = PFC_mean, y = value, color = Group, group = Group)) + 
  stat_smooth(aes(x = PFC_mean, y = value, color = Group, group = Group), method = "lm") +
  scale_color_manual(values = c("blue", "red")) +
  ylab("z-score") +
  facet_wrap(. ~ variable) + ylim(-2,2)
```



