---
title: "Age Differences in Functional Connectivity Metrics"
author: "Megan McMahon"
date: "1/13/2020"
output: html_document
---

# Contents
* [Differences in functional connectivity measures across age groups]
* [Rest-activity measures and cognition]
* [*1]
* [Network measures and cognition]
* [*2]
* [Rest-activity measures and functional connectivity networks]

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(reshape2)
library(corrplot)
library(beset)

load("~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2020-01-13.RData")

cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# load("~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2019-12-13.RData")
# bct <- read_csv('~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/rest/bct/bct_x.csv')
# d <- merge(d, bct, by = "record_id", all = TRUE)
# d$actquot <- d$actamp/d$actmesor
# d$Group <- factor(ifelse(d$record_id < 40000, 0, 1), labels = c("Young Adults", "Older Adults"))

# mem <- read_csv("~/Box/CogNeuroLab/Aging Decision Making R01/Data/memmatch_results.csv")
# mem$X1 <- NULL
# 
# mem %>%
#   group_by(record_id, cond) %>%
#   summarise_each(funs(mean(., na.rm = TRUE)), isCorrect) %>%
#   spread(cond, isCorrect) -> acc
# 
# colnames(acc) <- paste0("acc_cond_", colnames(acc))
# 
# mem %>%
#   group_by(record_id, cond) %>%
#   summarise_each(funs(mean(., na.rm = TRUE)), RT_c) %>%
#   spread(cond, RT_c) -> rt
# 
# colnames(rt) <- paste0("rt_cond_", colnames(rt))
# 
# d <- merge(d, acc, by.x = "record_id", by.y = "acc_cond_record_id")
# d <- merge(d, rt, by.x = "record_id", by.y = "rt_cond_record_id")
# save(d, file = "~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2019-12-25.RData")
#
# rpx <- read_csv("~/Box/CogNeuroLab/Aging Decision Making R01/Data/Actigraphy/Combined Export File.csv")
# 
# rpx %>%
#   filter(interval_type == "Sleep Summary", interval_number == "Average(n)") %>%
#   select(-data_start_date, -data_start_time, -start_date, -start_time, -end_date, -end_time) -> rpx_mean
# 
# head(rpx_mean)
# 
# d <- merge(d, select(rpx_mean, subject_id, sleep_time, total_ac, onset_latency, efficiency), by.x = "record_id", by.y = "subject_id", all = TRUE)
# d$sleep_efficiency <- d$efficiency
# d$efficiency <- NULL
# 
# save(d, file = "~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2020-01-13.RData")

ya_data <- d[d$Group == "Young Adults",]
oa_data <- d[d$Group == "Older Adults",]

```


# Differences in functional connectivity measures across age groups

```{r}
d %>%
  select(Group, matches("wb_")) %>%
  na.omit() %>%
  melt(id.vars = "Group") %>%
  ggplot(aes(color = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = value), size=1.2) + 
  facet_wrap( . ~ variable, scales = "free_y") +
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) + 
  scale_x_discrete(labels = c("YA", "OA")) + 
  ggtitle("Whole Brain")

d %>%
  select(Group, matches("dmn_")) %>%
  na.omit() %>%
  melt(id.vars = "Group") %>%
  ggplot(aes(color = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = value), size=1.2) + 
  facet_wrap( . ~ variable, scales = "free_y") +
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) + 
  scale_x_discrete(labels = c("YA", "OA")) +
  ggtitle("Default Mode Network")

d %>%
  select(Group, matches("fpn_")) %>%
  na.omit() %>%
  melt(id.vars = "Group") %>%
  ggplot(aes(color = Group, group = Group)) + 
  geom_boxplot(aes(x = Group, y = value), size=1.2) + 
  facet_wrap( . ~ variable, scales = "free_y") +
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) + 
  scale_x_discrete(labels = c("YA", "OA")) +
  ggtitle("Control Network")

t <- t.test(wb_participation_x ~ Group, data = d) ##
t
ggplot(d, aes(x = Group, y = wb_participation_x, color = Group)) +
  geom_boxplot() + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) +
  scale_x_discrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Participation \n Coefficient") + 
  labs(caption = (paste("t = ", round(t$statistic, 3), "p = ", round(t$p.value, 3))))

t <- t.test(wb_efficiency_x ~ Group, data = d) ##
t
ggplot(d, aes(x = Group, y = wb_efficiency_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) +
  scale_x_discrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round(t$statistic, 3), "p = ", round(t$p.value, 3))))

t <- t.test(dmn_efficiency_x ~ Group, data = d) ##
t
ggplot(d, aes(x = Group, y = dmn_efficiency_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) +
  scale_x_discrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round(t$statistic, 3), "p = ", round(t$p.value, 3))))

t <- t.test(dmn_modularity_x ~ Group, data = d) ##
t
ggplot(d, aes(x = Group, y = dmn_modularity_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) +
  scale_x_discrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round(t$statistic, 3), "p = ", round(t$p.value, 3))))

t <- t.test(fpn_participation_x ~ Group, data = d) ##
t
ggplot(d, aes(x = Group, y = fpn_participation_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) +
  scale_x_discrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round(t$statistic, 3), "p = ", round(t$p.value, 3))))

t <- t.test(fpn_betweenness_x ~ Group, data = d) ##
t
ggplot(d, aes(x = Group, y = fpn_betweenness_x, color = Group)) +
  geom_boxplot(size = 1.2) + 
  theme_classic() + 
  scale_colour_manual(values=c("blue", "red")) +
  scale_x_discrete(labels=c("YA", "OA")) + 
  xlab("Age Group") + ylab("Global \n Efficiency") + 
  theme(axis.text=element_text(size=12), plot.caption = element_text(size = 12)) +
  labs(caption = (paste("t = ", round(t$statistic, 3), "p = ", round(t$p.value, 3))))
```

# Rest-activity measures and cognition

## Older Adults
```{r}
alpha = 0.05

oa_cor <- select(oa_data, age, IS:RA, actquot, actamp:fact, matches("zscore|z_score|time_trails"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```
```{r}
alpha = 0.05

oa_cor <- select(oa_data, age, sleep_time, onset_latency, sleep_efficiency, matches("zscore|z_score|time_trails"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```


```{r}
oa_data %>%
  select(age, IS, matches("zscore|z_score")) %>%
  melt(id.vars = "IS") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = IS, y = value)) +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("IS and Neuropsych Measures")

oa_data %>%
  select(age, fact, matches("zscore|z_score")) %>%
  melt(id.vars = "fact") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = fact, y = value)) +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("F-statistic and Neuropsych Measures")

oa_data %>%
  select(age, RA, matches("zscore|z_score")) %>%
  melt(id.vars = "RA") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = RA, y = value)) +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("RA and Neuropsych Measures")

oa_data %>%
  select(age, IV, matches("zscore|z_score")) %>%
  melt(id.vars = "IV") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = IV, y = value)) +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("IV and Neuropsych Measures")

oa_data %>%
  select(age, sleep_time, matches("zscore|z_score")) %>%
  melt(id.vars = "sleep_time") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = sleep_time, y = value)) +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("Sleep Time and Neuropsych Measures")

oa_data %>%
  select(age, sleep_efficiency, matches("zscore|z_score")) %>%
  melt(id.vars = "sleep_efficiency") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = sleep_efficiency, y = value)) +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("Sleep Efficiency and Neuropsych Measures")
```

Trails B
```{r}
alpha = 0.05 

oa_cor <- select(oa_data, age, IS:RA, actquot, actamp:fact, sleep_time, sleep_efficiency, trails_b_z_score)
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```


```{r}
oa_data$TMT <- ifelse(oa_data$trails_b_z_score < median(oa_data$trails_b_z_score, na.rm = TRUE), "Low", "High")
ya_data$TMT <- ifelse(ya_data$trails_b_z_score < median(ya_data$trails_b_z_score, na.rm = TRUE), "Low", "High")
alpha = 0.05 

oa_data %>%
  na.omit(TMT) %>%
  select(age, IS:RA, actamp, actquot, fact, actalph, TMT) %>%
  melt(id.vars = "TMT") %>%
  ggplot() +
  theme_minimal() +
  geom_boxplot(aes(x = TMT, y = value)) +
  facet_wrap(. ~ variable, scales = "free_y") + 
  ggtitle("Rest-activity measures by TMT performance")
```

Out of curiosity from DTI...
```{r}
oa_data %>%
  select(age, actalph, matches("zscore|z_score|time_trails")) %>%
  melt(id.vars = "actalph") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = actalph, y = value)) +
  facet_wrap(. ~ variable, scales = "free_y") + 
  ggtitle("actalph and Neuropsych Measures")
```

## Young Adults

```{r}
alpha = 0.05

ya_cor <- select(ya_data, age, IS:RA, actquot, actamp:fact, vc_zscore, ds_zscore, trails_a_z_score, trails_b_z_score)
ya_cor <- ya_cor[complete.cases(ya_cor), ]
ya_mat <- cor(ya_cor)
ya_res <- cor.mtest(ya_mat, conf.level = (1-alpha))
corrplot(ya_mat, p.mat = ya_res$p, sig.level = alpha, insig = "blank", type = "upper")
```

```{r}
alpha = 0.05

ya_cor <- select(ya_data, age, sleep_time, onset_latency, sleep_efficiency, vc_zscore, ds_zscore, trails_a_z_score, trails_b_z_score)
ya_cor <- ya_cor[complete.cases(ya_cor), ]
ya_mat <- cor(ya_cor)
ya_res <- cor.mtest(ya_mat, conf.level = (1-alpha))
corrplot(ya_mat, p.mat = ya_res$p, sig.level = alpha, insig = "blank", type = "upper")
```

## *1

```{r}
summary(lm(trails_b_z_score ~ sleep_efficiency, data = ya_data)) # p = 0.0468, B < 0 ? 
summary(lm(trails_b_z_score ~ Group*sleep_efficiency, data = d)) # *

summary(lm(trails_b_z_score ~ sleep_time, data = ya_data)) # p = 0.0472, B < 0 ? 
summary(lm(trails_b_z_score ~ Group*sleep_time, data = d)) # .
```

# Network measures and cognition

## Older Adults
```{r}
alpha = 0.05

oa_cor <- select(oa_data, age, matches("wb_|dmn_|fpn_"),matches("zscore|z_score"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```


```{r}
oa_data %>%
  select(age, dmn_participation_x, matches("zscore|z_score")) %>%
  melt(id.vars = "dmn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = dmn_participation_x, y = value)) +
  stat_smooth(aes(x = dmn_participation_x, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("DMN Participation and Neuropsych Measures")
```

```{r}
summary(lm(ds_zscore ~ dmn_participation_x, data = oa_data)) #NS
summary(lm(ds_zscore ~ Group*dmn_participation_x, data = d)) #NS
```


```{r}
oa_data %>%
  select(age, fpn_participation_x, matches("zscore|z_score")) %>%
  melt(id.vars = "fpn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = fpn_participation_x, y = value)) +
  stat_smooth(aes(x = fpn_participation_x, y = value), method = "lm") +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("FPN Participation and Neuropsych Measures")
```

```{r}
summary(lm(trails_b_z_score ~ fpn_participation_x, data = oa_data)) # p = 0.0569

```


## Young Adults

```{r}
alpha = 0.05

ya_cor <- select(ya_data, age, matches("wb_|dmn_|fpn_"), vc_zscore, ds_zscore, trails_a_z_score, trails_b_z_score)
ya_cor <- ya_cor[complete.cases(ya_cor), ]
ya_mat <- cor(ya_cor)
ya_res <- cor.mtest(ya_mat, conf.level = (1-alpha))
corrplot(ya_mat, p.mat = ya_res$p, sig.level = alpha, insig = "blank", type = "upper")
```


```{r}
ya_data %>%
  select(age, fpn_participation_x, vc_zscore, ds_zscore, trails_a_z_score, trails_b_z_score) %>%
  melt(id.vars = "fpn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = fpn_participation_x, y = value)) +
  facet_wrap (. ~ variable, scales = "free_y") + 
  ggtitle("FPN Participation and Neuropsych Measures")
```

## *2

```{r}
summary(lm(trails_b_z_score ~ fpn_participation_x, data = ya_data)) #NS
summary(lm(trails_b_z_score ~ Group*fpn_participation_x, data = d)) #p = 0.0161
```


# Rest-activity measures and functional connectivity networks

## Older Adults
```{r}
alpha = 0.05

oa_cor <- select(oa_data, age, IS:RA, actamp:fact, actquot, matches("wb_|dmn_|fpn_"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```

```{r}
oa_data %>%
  select(age, IS:RA, actamp, actalph, actupmesor, fact, fpn_participation_x) %>%
  melt(id.vars = "fpn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = value, y = fpn_participation_x)) +
  facet_wrap (. ~ variable, scales = "free_x")
```



```{r}
oa_data %>%
  select(age, IS:RA, actamp, actalph, actupmesor, fact, dmn_participation_x) %>%
  melt(id.vars = "dmn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = value, y = dmn_participation_x)) +
  facet_wrap (. ~ variable, scales = "free_x")
```



## Young Adults
```{r}
ya_data %>%
  select(age, IS:RA, actamp, actalph, actupmesor, fact, fpn_participation_x) %>%
  melt(id.vars = "fpn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = value, y = fpn_participation_x)) +
  facet_wrap (. ~ variable, scales = "free_x")
```

```{r}
ya_data %>%
  select(age, IS:RA, actamp, actalph, actupmesor, fact, dmn_participation_x) %>%
  melt(id.vars = "dmn_participation_x") %>%
  ggplot() +
  theme_minimal() +
  geom_point(aes(x = value, y = dmn_participation_x)) +
  facet_wrap (. ~ variable, scales = "free_x")
```
