---
title: "Circadian Measures and DTI"
author: "Megan McMahon"
date: "12/3/2019"
output: html_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)
library(readr)
library(corrplot)
library(reshape2)
library(car)
library(beset)
library(psych)

load("~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2019-12-13.RData")

# load('~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data.RData')
# dti <- readxl::read_xlsx('~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/dwi/cr_fa_md.xlsx')
# dti <- merge(select(dti, record_id, age, matches("fa_mean|md_mean"), -matches("skel"), IS:RA), select(d, record_id, matches("zscore|z_score|trails|cvlt|ds")), by = "record_id", all = TRUE)
# d <- c()
# 
# cr <- read_csv("~/Box/CogNeuroLab/Aging Decision Making R01/Data/CR/cosinor_measures_2019-12-13.csv")
# d <- merge(dti, cr, by = "record_id", all = TRUE)
# d$fa_mean_cc <- (d$fa_mean_3 + d$fa_mean_4 + d$fa_mean_5)/3
# d$md_mean_cc <- (d$md_mean_3 + d$md_mean_4 + d$md_mean_5)/3
# 
# d <- merge(d, pvt, by = "record_id", all = TRUE)
# d <- merge(d, ccnorm, by = "record_id", all = TRUE)
# 
# # d <- select(dti, -fa_mean_3_skel, -fa_mean_4_skel, -fa_mean_5_skel, -md_mean_3_skel, -md_mean_4_skel, -md_mean_5_skel)
# d$Group <- factor(ifelse(d$record_id < 40000, 0, 1), label = c("Young Adults", "Older Adults"))
# save(d, file = "~/Box/CogNeuroLab/Aging Decision Making R01/Data/combined_data_2019-12-13.RData")

ya_data <- d[d$Group == "Young Adults", ]
oa_data <- d[d$Group == "Older Adults", ]

# remove actbeta outlier
# summary(d$actbeta)
# d$record_id[d$actbeta == max(d$actbeta)]
# d[d$record_id == 40758,] <- NA
```



```{r}
# correlation plots
alpha = 0.05

ya_cor <- select(ya_data, age, IS:IV, actamp:fact, trails_b_z_score,  matches("md_mean|fa_mean"))
ya_cor <- ya_cor[complete.cases(ya_cor), ]
ya_mat <- cor(ya_cor)
ya_res <- cor.mtest(ya_mat, conf.level = (1-alpha))
corrplot(ya_mat, p.mat = ya_res$p, sig.level = alpha, insig = "blank", type = "upper")

oa_cor <- select(oa_data, age, IS:IV, actamp:fact, matches("zscore|z_score|md_mean|fa_mean"))
oa_cor <- oa_cor[complete.cases(oa_cor), ]
oa_mat <- cor(oa_cor)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
#addCoef.col = TRUE, number.cex = .6
```

## Confidence Intervals for Correlations
### In older adults, which FA or MD measures are correlated with neuropsych measures?
```{r}

library(corxplor)
oa_data <- filter(d, Group == "Older Adults")
oa_cor_data <- select(oa_data, matches("fa_mean|md_mean"), matches("zscore|z_score"))
boot <- corxplor::cor_boot(x = oa_cor_data, y = NULL, use = "pairwise", method = "pearson",
                     n_rep = 1000, conf = 0.95, seed = 42, n_cores = NULL)
boot
```

## Mediation model? Duration of peak activity & CVLT
```{r}
library(beset)
stepdata <- select(oa_data, age, IS:RA, actalph:fact, -actwidthratio, -rsqact, -fa_mean_cc, matches("md_mean|fa_mean"), cvlt_zscore)
sum(complete.cases(stepdata))

mod <- beset_lm(cvlt_zscore ~ ., data = stepdata, n_folds = sum(complete.cases(stepdata)))
plot(mod)
#return the model with the smallest number of parameters that is within one standard error of the model with the lowest cross-validation error (the “1-SE rule”).
summary(mod, n_folds = sum(complete.cases(stepdata)))
#without 1-SE rule
summary(mod, oneSE = FALSE, n_folds = sum(complete.cases(stepdata))) #age, alpha, md mean 4

#mediation model - md not mediator
# Y ~ X
lm01 <- lm(cvlt_zscore ~ actalph, data = oa_cor) #alpha+
validate(lm01)
summary(lm01)
# M ~ X
lm02 <- lm(md_mean_cc ~ actalph, data = oa_cor) #alpha+, age.
validate(lm02)
summary(lm02)
# Y ~ X + Y, best model from LOOCV stepwise regression
lm03 <- lm(cvlt_zscore ~ actalph + md_mean_cc, data = oa_cor) #alpha+, md+NS
validate(lm03)
summary(lm03)

medmod <- mediate(cvlt_zscore ~ actalph + (md_mean_cc), data = oa_cor, n.iter=500)
print(medmod, short = FALSE)

medmod2 <- mediate(cvlt_zscore ~ actalph + (md_mean_4), data = oa_cor, n.iter=500)
print(medmod2, short = FALSE)

summary(lm(cowat_zscore ~ fa_mean_cc, data = oa_data))
summary(lm(cowat_zscore ~ fa_mean_cc + actalph, data = oa_data))

d %>%
  na.omit() %>%
  filter(Group == "Older Adults") %>%
  ggplot(aes(group = Group, color = Group)) +
  geom_point(aes(x = actalph, y = cvlt_sdelay_recall_zscore, group = Group, color = Group)) +
  stat_smooth(aes(x = actalph, y = cvlt_sdelay_recall_zscore, group = Group, color= Group), method = "lm") +
  theme_classic() +
  scale_color_manual(values = c("blue")) +
  xlab("Width (alpha)") + ylab("CVLT Z-score") +
  theme(legend.position = "none") #+
  #ggsave("~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/ohbm2020/ya-fact-fa.png", width = 3, height = 2.5)

summary(d$actalph)
oa_data$record_id[oa_data$actalph == max(oa_data$actalph)]
```


### In older adults, which CR measures are correlated with FA or MD?
```{r}
oa_cor_data <- select(oa_data, IS:RA, actamp:fact, matches("fa_mean|md_mean"))
boot <- corxplor::cor_boot(x = oa_cor_data, y = NULL, use = "pairwise", method = "pearson",
                     n_rep = 1000, conf = 0.95, seed = 42, n_cores = NULL)
boot
```

## Regression Models
```{r}
lmcc <- lm(md_mean_cc ~ age + actalph, data = oa_data)
summary(lmcc)

lmcc2 <- lm(fa_mean_cc ~ age + actalph, data = oa_data)
summary(lmcc2)

lm1 <- lm(md_mean_4 ~ age + actalph, data = oa_data)
summary(lm1)
AIC(lm1)
d %>%
  na.omit() %>%
  select(Group, md_mean_3, md_mean_4, md_mean_5, actalph) %>%
  melt(id.vars = c("Group", "actalph")) %>%
  ggplot(aes(color = Group, group = Group)) +
  geom_point(aes(x = actalph, y = value, group = Group, color = Group)) +
  stat_smooth(aes(x = actalph, y = value, group = Group, color= Group), method = "lm") + 
  scale_color_manual(values = c("blue", "red")) +
  facet_wrap(Group ~ variable, scales = "free_y") +
  xlab("Width (alpha)") + ylab("Mean Diffusivity") 
```


width (alpha) and width-ratio are related
```{r}
lm2 <- lm(md_mean_4 ~ age + actwidthratio, data = oa_data)
summary(lm2)
d %>%
  na.omit() %>%
  select(Group, md_mean_3, md_mean_4, md_mean_5, actwidthratio) %>%
  melt(id.vars = c("Group", "actwidthratio")) %>%
  ggplot(aes(color = Group, group = Group)) +
  geom_point(aes(x = actwidthratio, y = value, group = Group, color = Group)) +
  stat_smooth(aes(x = actwidthratio, y = value, group = Group, color= Group), method = "lm") + 
  scale_color_manual(values = c("blue", "red")) +
  facet_wrap(Group ~ variable, scales = "free_y") +
  xlab("Width-ratio") + ylab("Mean Diffusivity") 
```


```{r}
lm3 <- lm(fa_mean_4 ~ age + actalph, data = oa_data)
summary(lm3) # *
d %>%
  na.omit() %>%
  select(Group, fa_mean_3, fa_mean_4, fa_mean_5, actalph) %>%
  melt(id.vars = c("Group", "actalph")) %>%
  ggplot() +
  geom_point(aes(x = actalph, y = value, group = Group, color = Group)) +
  stat_smooth(aes(x = actalph, y = value, group = Group, color= Group), method = "lm") + 
  scale_color_manual(values = c("blue", "red")) +
  facet_wrap(Group ~ variable, scales = "free_y") +
  xlab("Width (alpha)") + ylab("Fractional Anisotropy") 
```

## LOOCV Stepwise Regression Models
```{r}
#older adults
#mean diffusivity
#alpha
stepdata <- select(oa_data, age, actalph:fact, -rsqact, -actwidthratio, md_mean_cc)
mod <- beset_lm(md_mean_cc ~ ., data = stepdata, n_folds = 35, force_in = "age")
summary(mod, oneSE = FALSE, n_folds = 35) 
summary(lm(md_mean_cc ~ actalph + age, data = oa_data))
#fractional anisotropy
#fact
stepdata <- select(oa_data, age, actalph:fact, -rsqact, -actwidthratio, fa_mean_cc)
mod <- beset_lm(fa_mean_cc ~ ., data = stepdata, n_folds = 35, force_in = "age")
summary(mod, oneSE = FALSE, n_folds = 35) 
summary(lm(fa_mean_cc ~ actalph + age, data = oa_data))
#volume
#hodgepodge
stepdata <- select(oa_data, age, actalph:fact, -rsqact, -actwidthratio, CC_Total)
mod <- beset_lm(CC_Total ~ ., data = stepdata, n_folds = 35)
summary(mod, oneSE = FALSE, n_folds = 35) 
summary(lm(CC_Total ~ age + actalph, data = oa_data))
```


```{r}
#young adults
#mean diffusivity
#alpha
stepdata <- select(ya_data, age, actalph:fact, -rsqact, -actwidthratio, md_mean_cc)
mod <- beset_lm(md_mean_cc ~ ., data = stepdata, n_folds = 29)
summary(mod, oneSE = FALSE, n_folds = 29) 
summary(lm(md_mean_cc ~ actalph, data = ya_data))
#fractional anisotropy
#fact
stepdata <- select(ya_data, age, actalph:fact, -rsqact, -actwidthratio, fa_mean_cc)
mod <- beset_lm(fa_mean_cc ~ ., data = stepdata, n_folds = 29)
summary(mod, oneSE = FALSE, n_folds = 29) 
summary(lm(fa_mean_cc ~ fact, data = ya_data))
#volume
#hodgepodge
stepdata <- select(ya_data, age, actalph:fact, -rsqact, -actwidthratio, CC_Total)
mod <- beset_lm(CC_Total ~ ., data = stepdata, n_folds = 29)
summary(mod, oneSE = FALSE, n_folds = 29) 
summary(lm(CC_Total ~ IS + IV + actalph + fact, data = ya_data))

```

## Any correlations with neuropsych measures?
```{r, include=FALSE}
# correlation plots
# alpha = 0.05
# 
# d$ef <- (d$trails_b_z_score + d$ds_zscore)/2
# oa_data <- filter(d, Group == "Older Adults")
# 
# 
# oa_cor <- select(oa_data, actalph, ef, matches("cvlt|ds|trails"))
# oa_cor <- oa_cor[complete.cases(oa_cor), ]
# oa_mat <- cor(oa_cor)
# oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
# corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
# 
# oa_mat <- cor(select(oa_cor, matches("fa_mean|md_mean|CC_"), matches("zscore|z_score")))
# oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
# corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
#addCoef.col = TRUE, number.cex = .6
```


## Do cowat and width (alpha) account for separate variance in FA?
```{r}
summary(lm(fa_mean_4 ~ cowat_zscore + actalph, data = oa_data))
```

## Corpus Callosum Volume Relationships
```{r}
alpha = 0.05
oa_cor_data <- select(oa_data, IS:RA, actamp:fact, matches("CC_"))
oa_cor_data <- oa_cor_data[complete.cases(oa_cor_data),]
oa_mat <- cor(oa_cor_data)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
# CC Mid Anterior actalph, actwidthratio, actbeta

ya_cor_data <- select(ya_data, IS:RA, actamp:fact, matches("CC_"))
ya_cor_data <- ya_cor_data[complete.cases(ya_cor_data),]
ya_mat <- cor(ya_cor_data)
ya_res <- cor.mtest(ya_mat, conf.level = (1-alpha))
corrplot(ya_mat, p.mat = ya_res$p, sig.level = alpha, insig = "blank", type = "upper")
# CC Anterior and IS, actamp, RA, fact
```


```{r}
summary(lm(CC_Total ~ age + actalph, data = oa_data))
```


## Neuropsych z-scores and corpus callosum volume measures in OA
```{r}
alpha = 0.05

oa_cor_data <- select(oa_data, matches("zscore|z_score"), matches("CC_"))
oa_mat <- cor(oa_cor_data)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")

```


```{r}
#age the only significant predictor of CC total volume
library(beset)
mod_fs1 <- beset_lm(CC_Total ~ ., data = stepdata, n_folds = 38)#, force_in = "age")
summary(mod_fs1, n_folds = 38) #age
summary(mod_fs1, n_folds = 38, oneSE = FALSE) #age
plot(mod_fs1, n_folds = 38, oneSE = FALSE)
```

Best model without 1 SE rule - age (S), RA, width (S) predict total CC volume


## CR Measures and CC Volume
```{r}
#No significant interaction effects
summary(lm(CC_Total ~ IS * Group, data = d2))
summary(lm(CC_Total ~ IV * Group, data = d2))
summary(lm(CC_Total ~ RA * Group, data = d2))
summary(lm(CC_Total ~ fact * Group, data = d2))
summary(lm(CC_Central ~ fact * Group, data = d2))

#Significant age group effect
summary(lm(CC_Total ~ IS + Group, data = d2))
summary(lm(CC_Total ~ IV + Group, data = d2))
summary(lm(CC_Total ~ RA + Group, data = d2))
summary(lm(CC_Total ~ fact + Group, data = d2))
summary(lm(CC_Central ~ fact + Group, data = d2))

#Significant effect of age
summary(lm(CC_Total ~ actalph, data = oa_data)) #p = 0.06
summary(lm(CC_Total ~ actalph+age, data = oa_data)) #but effect goes away when include age

#from corplots
summary(lm(CC_Mid_Anterior ~ actalph + age, data = oa_data)) #NS
summary(lm(CC_Central ~ actalph + age, data = oa_data)) #NS

summary(lm(CC_Total ~ actwidthratio + age, data = ya_data)) #NS
summary(lm(CC_Total ~ actbeta + age, data = ya_data)) #NS

```
```{r, echo = FALSE, include = FALSE}
oa_data$FA <- factor(ifelse(oa_data$fa_mean_4 < median(oa_data$fa_mean_4, na.rm = TRUE), -1, 1), labels = c("Low", "High"))
oa_data$Width <- factor(ifelse(oa_data$actalph < median(oa_data$actalph, na.rm = TRUE), -1, 1), labels = c("Low", "High"))


oa_data %>% 
  subset(!is.na(Width)) %>%
  subset(!is.na(FA)) %>%
  ggplot() +
  aes(x = Width, color = FA, group = FA, y = cowat_zscore) +
  stat_summary(fun.y = mean, na.rm = TRUE, geom = "point") +
  stat_summary(fun.y = mean, na.rm = TRUE, geom = "line") + 
  scale_color_manual(values = c("blue", "red")) +
  xlab('Width (alpha)') + ylab('COWAT z-score')

```


## PVT
Predictors of relative response time and false starts?
```{r}

alpha = 0.05

oa_cor_data <- select(oa_data, rt_mean, fs, IS:RA, actamp:fact)
oa_cor_data <- oa_cor_data[complete.cases(oa_cor_data), ]
oa_mat <- cor(oa_cor_data)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")

oa_cor_data <- select(oa_data, rt_mean, fs, matches("fd_mean|md_mean|CC_"))
oa_cor_data <- oa_cor_data[complete.cases(oa_cor_data), ]
oa_mat <- cor(oa_cor_data)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")

summary(lm(rt_mean ~ md_mean_sca, data = oa_data))

stepdata <- select(oa_data, md_mean_sca, actamp:fact, -actdownmesor, -actwidthratio, -rsqact)
mod <- beset_lm(md_mean_sca ~ ., data = stepdata, n_folds = sum(complete.cases(stepdata)))
plot(mod)
#return the model with the smallest number of parameters that is within one standard error of the model with the lowest cross-validation error (the “1-SE rule”).
summary(mod, n_folds = sum(complete.cases(stepdata)))
#without 1-SE rule
summary(mod, oneSE = FALSE, n_folds = sum(complete.cases(stepdata))) 
summary(lm(md_mean_sca ~ actamp, data = oa_data)) #NS

stepdata <- select(oa_data, md_mean_sca, IV:RA)
mod <- beset_lm(md_mean_sca ~ ., data = stepdata, n_folds = sum(complete.cases(stepdata)))
plot(mod)
#return the model with the smallest number of parameters that is within one standard error of the model with the lowest cross-validation error (the “1-SE rule”).
summary(mod, n_folds = sum(complete.cases(stepdata)))
#without 1-SE rule
summary(mod, oneSE = FALSE, n_folds = sum(complete.cases(stepdata)))
summary(lm(md_mean_sca ~ IV + RA, data = oa_data)) #RA
```

## 12/10 To Do:
- Within age group, look at raw TMT scores (**done**)
- Double check PVT 
- Rerun CR measures with end time from redcap (**done**)
- Rerun CC volume adjusting for ICV (**done**)

```{r}
tmt <- select(d, record_id, matches("trails|ds"))
head(tmt)

d3 <- c()
dti <- readxl::read_xlsx('~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/dwi/cr_fa_md.xlsx')

d3 <- merge(dti, tmt, by = "record_id", no.dups = FALSE)
d3$time_trails_b <- as.numeric(d3$time_trails_b)
d3$error_trails_b <- as.numeric(d3$error_trails_b)
d3$Group <- factor(ifelse(d3$record_id < 40000, 0, 1), label = c("Young Adults", "Older Adults"))
ya_data <- d3[d3$Group == "Young Adults", ]
oa_data <- d3[d3$Group == "Older Adults", ]

alpha = 0.05

oa_cor_data <- select(oa_data, -record_id, -files, -Group, -matches("skel"))
oa_mat <- cor(oa_cor_data)
oa_res <- cor.mtest(oa_mat, conf.level = (1-alpha))
corrplot(oa_mat, p.mat = oa_res$p, sig.level = alpha, insig = "blank", type = "upper")
```

## Figures
```{r}
d2 <- d

#both - different width effects on md
d2 %>%
  ggplot(aes(group = Group, color = Group)) +
  geom_point(aes(x = actalph, y = md_mean_cc, group = Group, color = Group)) +
  stat_smooth(aes(x = actalph, y = md_mean_cc, group = Group, color= Group), method = "lm") +
  theme_classic() +
  scale_color_manual(values = c("blue", "red")) +
  xlab("Width (alpha)") + ylab("CC Mean Diffusivity") + xlim(-1,0.25) +
  ggsave("~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/ohbm2020/both-alpha-md.png", width = 3, height = 2.5)

#older adults
d2 %>%
  filter(Group == "Older Adults") %>%
  ggplot(aes(group = Group, color = Group)) +
  geom_point(aes(x = actalph, y = md_mean_cc, group = Group, color = Group)) +
  stat_smooth(aes(x = actalph, y = md_mean_cc, group = Group, color= Group), method = "lm") +
  theme_classic() +
  scale_color_manual(values = c("red")) +
  xlab("Width (alpha)") + ylab("CC Mean Diffusivity") + xlim(-1,0) +
  theme(legend.position = "none") +
  ggsave("~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/ohbm2020/oa-alpha-md.png", width = 3, height = 2.5)

d2 %>%
  filter(Group == "Older Adults") %>%
  ggplot(aes(group = Group, color = Group)) +
  geom_point(aes(x = actalph, y = fa_mean_cc, group = Group, color = Group)) +
  stat_smooth(aes(x = actalph, y = fa_mean_cc, group = Group, color= Group), method = "lm") +
  theme_classic() +
  scale_color_manual(values = c("red")) +
  xlab("Width (alpha)") + ylab("CC Fractional Anisotropy") + xlim(-1,0) +
  theme(legend.position = "none") +
  ggsave("~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/ohbm2020/oa-alpha-fa.png", width = 3, height = 2.5)

#young adults
d2 %>%
  filter(Group == "Young Adults") %>%
  ggplot(aes(group = Group, color = Group)) +
  geom_point(aes(x = actalph, y = md_mean_cc, group = Group, color = Group)) +
  stat_smooth(aes(x = actalph, y = md_mean_cc, group = Group, color= Group), method = "lm") +
  theme_classic() +
  scale_color_manual(values = c("blue")) +
  xlab("Width (alpha)") + ylab("CC Mean Diffusivity") + xlim(-1,0.25) +
  theme(legend.position = "none") +
  ggsave("~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/ohbm2020/ya-alpha-md.png", width = 3, height = 2.5)

d2 %>%
  filter(Group == "Young Adults") %>%
  ggplot(aes(group = Group, color = Group)) +
  geom_point(aes(x = fact, y = fa_mean_cc, group = Group, color = Group)) +
  stat_smooth(aes(x = fact, y = fa_mean_cc, group = Group, color= Group), method = "lm") +
  theme_classic() +
  scale_color_manual(values = c("blue")) +
  xlab("Robustness (F-statistic)") + ylab("CC Fractional Anisotropy") + xlim(500,8500) +
  theme(legend.position = "none") +
  ggsave("~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/ohbm2020/ya-fact-fa.png", width = 3, height = 2.5)
```


