---
title: "Rest-Activity Measures and White Matter Microstructure Across the Lifespan"
author: "Megan McMahon"
date: "10/5/2020"
output: html_document
---

```{r setup, include=FALSE}
setwd(dirname(rstudioapi::getSourceEditorContext()$path))

source("load.R", local = knitr::knit_global())
source("clean.R", local = knitr::knit_global())
source("tables.R", local = knitr::knit_global())
```

## Exploring Some Histograms
```{r warning = FALSE}
d %>%
  select(age, years_educ, sleep_time_mean_sleep, efficiency_mean_sleep, onset_latency_mean_sleep, total_ac_mean_active, actamp, actalph, actbeta, actmesor, actphi, actupmesor, actdownmesor, actmin, fact, IS, IV, RA, L5, M10) %>%
  keep(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram()

```

## Exploring Some Histograms by Group
```{r warning = FALSE}
d %>%
  select(age, years_educ, sleep_time_mean_sleep, efficiency_mean_sleep, onset_latency_mean_sleep, total_ac_mean_active, actamp, actalph, actbeta, actmesor, actphi, actupmesor, actdownmesor, actmin, fact, IS, IV, RA, L5, M10, Group) %>%
  melt(id.vars = "Group") %>%
  ggplot(aes(value, group = Group, fill = Group, alpha = 0.75)) +
    facet_wrap(~ variable, scales = "free") +
    geom_density() + 
  theme_classic() + scale_fill_brewer(palette = "Set1")

```

## Normality Tests
```{r warning = FALSE}
d %>%
  select(age, years_educ, sleep_time_mean_sleep, efficiency_mean_sleep, onset_latency_mean_sleep, total_ac_mean_active, actamp, actalph, actbeta, actmesor, actphi, actupmesor, actdownmesor, actmin, fact, IS, IV, RA, L5, M10) %>%
  keep(is.numeric) %>% 
  shapiro_test(age, years_educ, sleep_time_mean_sleep, efficiency_mean_sleep, onset_latency_mean_sleep, total_ac_mean_active, actamp, actalph, actbeta, actmesor, actphi, actupmesor, actdownmesor, actmin, fact, IS, IV, RA, L5, M10)
```

## Demographics
```{r}
tab1
```

## Health Characteristics
```{r}
tab2
```

## Sleep and Rest-Activity Rhythm Characteristics
```{r}
tab3
```

## Microstructure Characteristics
```{r}
tab4
```

## Neuropsych and PVT Results
```{r}
tab5
```

## Corpus Callosum Volume and Rhythm Amplitude
```{r warning = FALSE}
d %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = cc_vol, group = Group, color = Group, shape = Group), size = 2) + 
  stat_smooth(aes(x = actamp, y = cc_vol, group = Group, color = Group), method = "lm") + 
  theme_classic() + xlab("Amplitude") + ylab("Corpus Callosum Volume") +
  scale_color_brewer(palette="Set1") #+ 
  #ggsave(paste0(figs_dir, "amp_ccvol.png"), dpi=300, height=4, width=6, units="in")

```


## Corpus Callosum FA and Rhythm Amplitude
```{r warning = FALSE}
d %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = cc_fa, group = Group, color = Group, shape = Group), size = 2) + 
  stat_smooth(aes(x = actamp, y = cc_fa, group = Group, color = Group), method = "lm") + 
  theme_classic() + xlab("Amplitude") + ylab("Corpus Callosum FA") +
  scale_color_brewer(palette="Set1") +
  #theme(legend.position = c(0.9, 0.2)) + # for OHBM poster
  #ggsave(paste0(figs_dir, "amp_cc_fa2.png"), dpi=300, height=4, width=6, units="in") + # for OHBM poster
  ggsave(paste0(figs_dir, "amp_cc_fa.png"), dpi=300, height=4, width=6, units="in")
```

### No significant sex differences
```{r warning = FALSE}
d %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = cc_fa, group = sex, color = sex, shape = sex), size = 2) + 
  stat_smooth(aes(x = actamp, y = cc_fa, group = sex, color = sex), method = "lm") + 
  theme_classic() + xlab("Amplitude") + ylab("Corpus Callosum FA") +
  scale_color_brewer(palette="Set1") +
  facet_wrap(. ~ Group)
```


## Mean FA in other areas with significant clusters showing association between FA and rhythm amplitude
```{r warning = FALSE}
d %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = coronaradiata_fa, group = Group, color = Group, shape = Group), size = 2) + 
  stat_smooth(aes(x = actamp, y = coronaradiata_fa, group = Group, color = Group), method = "lm") + 
  theme_classic() + xlab("Amplitude") + ylab("Corona Radiata FA") +
  scale_color_brewer(palette="Set1") 

d %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = externalcapsule_fa, group = Group, color = Group, shape = Group), size = 2) + 
  stat_smooth(aes(x = actamp, y = externalcapsule_fa, group = Group, color = Group), method = "lm") + 
  theme_classic() + xlab("Amplitude") + ylab("External Capsule FA") +
  scale_color_brewer(palette="Set1") 

d %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = postthalamicradiation_fa, group = Group, color = Group, shape = Group), size = 2) + 
  stat_smooth(aes(x = actamp, y = postthalamicradiation_fa, group = Group, color = Group), method = "lm") + 
  theme_classic() + xlab("Amplitude") + ylab("Post-Thalamic Radiation FA") +
  scale_color_brewer(palette="Set1") 
```

## Corpus Callosum MD and Rhythm Amplitude - NS
```{r warning = FALSE}
d %>%
  filter(actamp < 3) %>%
  ggplot() + 
  geom_point(aes(x = actamp, y = cc_md, group = Group, color = Group)) + 
  #stat_smooth(aes(x = actamp, y = trails_b_z_score, group = Group, color = Group), method = "lm") +
  theme_classic() + xlab("Amplitude") + ylab("Corpus Callosum MD") +
  scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") +
  facet_wrap(.~Group, scales = "fixed") #+
#ggsave(paste0(figs_dir, "amp_tmtbz.png"), dpi=300, height=4, width=8, units="in")
```

## Corpus Callosum MD and Intradaily Variability
```{r warning = FALSE}
d %>%
  ggplot() + 
  geom_point(aes(x = IV, y = cc_md, group = Group, color = Group, shape = Group)) + 
  stat_smooth(aes(x = IV, y = cc_md, group = Group, color = Group), method = "lm") +
  theme_classic() + xlab("Intradaily Variability") + ylab("Corpus Callosum MD") +
  scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") +
  #facet_wrap(.~Group, scales = "fixed") #+
  ggsave(paste0(figs_dir, "IV_MD_CC.png"), dpi=300, height=4, width=8, units="in")
```

## MD in other regions and Intradaily Variability
```{r warning = FALSE}
d %>%
  ggplot() + 
  geom_point(aes(x = IV, y = corona_radiata_md, group = Group, color = Group, shape = Group)) + 
  stat_smooth(aes(x = IV, y = corona_radiata_md, group = Group, color = Group), method = "lm") +
  theme_classic() + xlab("Intradaily Variability") + ylab("Anterior Corona Radiata MD") +
  scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") +
  #facet_wrap(.~Group, scales = "fixed") #+
  ggsave(paste0(figs_dir, "IV_MD_ACR.png"), dpi=300, height=4, width=8, units="in")

d %>%
  ggplot() + 
  geom_point(aes(x = IV, y = superior_long_fasciculus_md, group = Group, color = Group, shape = Group)) + 
  stat_smooth(aes(x = IV, y = superior_long_fasciculus_md, group = Group, color = Group), method = "lm") +
  theme_classic() + xlab("Intradaily Variability") + ylab("Superior Longitudinal \nFasciculus MD") +
  scale_color_brewer(palette="Set1") + scale_fill_brewer(palette="Set1") +
  #facet_wrap(.~Group, scales = "fixed") #+
  ggsave(paste0(figs_dir, "IV_MD_SLF.png"), dpi=300, height=4, width=8, units="in")
```


