---
title: "Hippocampal volume and rest-activity rhythms"
author: "Megan McMahon"
date: "3/9/2021"
output: html_document
---

This analysis uses data from our NIA study. Here we are looking at hippocampal volume derived from the Freesurfer fsaverage5 parcellation in relation to aspects of rest-activity rhythms in both younger and older adults.

We use an an adjusted HC volume as documented in [Brehmer et al. (2020)](https://doi.org/10.1016/j.neuroimage.2019.116475)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(tidyverse)
library(RColorBrewer)
library(beset)

```

```{r}
dataDir <- '~/Box/CogNeuroLab/Aging Decision Making R01/data/'
df <- readr::read_csv(paste0(dataDir, 'dataset_2020-10-10.csv'))
fsvol <- readr::read_delim('/Volumes/schnyer/Aging_DecMem/Scan_Data/BIDS/derivatives/freesurfer/aseg_vol_table.txt', delim = '\t')
fsvol$record_id <- substr(fsvol$`Measure:volume`, 5, 10)
fsvol$record_id

df1 <- merge(df, fsvol, by = 'record_id', all = TRUE)

```

```{r}
colnames(fsvol)

```

## Total HC volume

```{r}
df1$hc_vol <- df1$`Left-Hippocampus` + df1$`Right-Hippocampus`
df1$thalamus_vol <- df1$`Left-Thalamus-Proper` + df1$`Right-Thalamus-Proper`
df1$caudate_vol <- df1$`Left-Caudate` + df1$`Right-Caudate`
df1$putamen_vol <- df1$`Left-Putamen` + df1$`Right-Putamen`

```

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `Group`, y = `hc_vol`, group = `Group`, color = `Group`))  +
  geom_boxplot() +
  scale_color_brewer(palette='Set1')

```

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `Group`, y = `thalamus_vol`, group = `Group`, color = `Group`))  +
  geom_boxplot() +
  scale_color_brewer(palette='Set1')

```

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `Group`, y = `putamen_vol`, group = `Group`, color = `Group`))  +
  geom_boxplot() +
  scale_color_brewer(palette='Set1')

```

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `Group`, y = `caudate_vol`, group = `Group`, color = `Group`))  +
  geom_boxplot() +
  scale_color_brewer(palette='Set1')

```

## Adjusted HC volume

Adjusted HC volume = raw HC volume – b X (ICV–average ICV), where b is the slope of regression of the raw HC volume on ICV.

```{r}


hc_icv_reg <- lm(EstimatedTotalIntraCranialVol ~ hc_vol, data = df1)
hc_b <- as.numeric(hc_icv_reg$coefficients['hc_vol'])
df1$hc_vol_adj <- df1$hc_vol - hc_b * (df1$EstimatedTotalIntraCranialVol - mean(df1$EstimatedTotalIntraCranialVol, na.rm = TRUE))

thalamus_icv_reg <- lm(EstimatedTotalIntraCranialVol ~ thalamus_vol, data = df1)
thalamus_b <- as.numeric(thalamus_icv_reg$coefficients['thalamus_vol'])
df1$thalamus_vol_adj <- df1$thalamus_vol - thalamus_b * (df1$EstimatedTotalIntraCranialVol - mean(df1$EstimatedTotalIntraCranialVol, na.rm = TRUE))

caudate_icv_reg <- lm(EstimatedTotalIntraCranialVol ~ caudate_vol, data = df1)
caudate_b <- as.numeric(caudate_icv_reg$coefficients['caudate_vol'])
df1$caudate_vol_adj <- df1$caudate_vol - caudate_b * (df1$EstimatedTotalIntraCranialVol - mean(df1$EstimatedTotalIntraCranialVol, na.rm = TRUE))

putamen_icv_reg <- lm(EstimatedTotalIntraCranialVol ~ putamen_vol, data = df1)
putamen_b <- as.numeric(putamen_icv_reg$coefficients['putamen_vol'])
df1$putamen_vol_adj <- df1$putamen_vol - putamen_b * (df1$EstimatedTotalIntraCranialVol - mean(df1$EstimatedTotalIntraCranialVol, na.rm = TRUE))

```


```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `Group`, y = `hc_vol_adj`, group = `Group`, color = `Group`))  +
  geom_boxplot() +
  scale_color_brewer(palette='Set1')
```

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `Group`, y = `thalamus_vol_adj`, group = `Group`, color = `Group`))  +
  geom_boxplot() +
  scale_color_brewer(palette='Set1')
```

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `Group`, y = `putamen_vol_adj`, group = `Group`, color = `Group`))  +
  geom_boxplot() +
  scale_color_brewer(palette='Set1')
```


```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `Group`, y = `caudate_vol_adj`, group = `Group`, color = `Group`))  +
  geom_boxplot() +
  scale_color_brewer(palette='Set1')
```

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot() + 
  geom_boxplot(aes(x = `sex`, y = `hc_vol_adj`, group = `sex`, color = `sex`))  +
  scale_color_brewer(palette='Set1')

```

## HC volume and age

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `age`, y = `hc_vol`, color = `Group`, group = `Group`)) + 
  geom_point() +
  scale_color_brewer(palette='Set1') +
  xlab('Age') + ylab('Hippocampal Volume')

```

```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `age`, y = `thalamus_vol`, color = `Group`, group = `Group`)) + 
  geom_point() +
  scale_color_brewer(palette='Set1') +
  xlab('Age') + ylab('Thalamus Volume')

df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `age`, y = `putamen_vol`, color = `Group`, group = `Group`)) + 
  geom_point() +
  scale_color_brewer(palette='Set1') +
  xlab('Age') + ylab('Putamen Volume')

df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `age`, y = `caudate_vol`, color = `Group`, group = `Group`)) + 
  geom_point() +
  scale_color_brewer(palette='Set1') +
  xlab('Age') + ylab('Caudate Volume')
```


```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `age`, y = `hc_vol_adj`, color = `Group`, group = `Group`)) + 
  geom_point() +
  scale_color_brewer(palette='Set1') +
  xlab('Age') + ylab('Adjusted Hippocampal Volume')

```


```{r}
df1 %>%
  drop_na(Group) %>%
  ggplot(aes(x = `years_educ`, y = `hc_vol`, color = `Group`, group = `Group`)) + 
  geom_point() +
  stat_smooth(method='lm') +
  scale_color_brewer(palette='Set1') +
  xlab('') + ylab('')

```

## Rest-activity rhythms vs. HC volume
```{r}
df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actamp`, y = `hc_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actamp`, y = `thalamus_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actamp`, y = `putamen_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actamp`, y = `caudate_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')
```


```{r}
df1$actquot <- df1$actamp / df1$actmesor

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actquot`, y = `hc_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

```

```{r}
summary(lm(hc_vol_adj ~ actquot*Group, data = df1))
summary(lm(hc_vol_adj ~ actquot + Group, data = df1))

```


```{r}
df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `fact`, y = `hc_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

```

```{r}
df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `IS`, y = `hc_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `IS`, y = `thalamus_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `IS`, y = `putamen_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `IS`, y = `caudate_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

```

```{r}
df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actupmesor`, y = `hc_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actupmesor`, y = `thalamus_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actupmesor`, y = `caudate_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')

df1 %>%
  drop_na(Group) %>%
  filter(actamp < 3) %>%
  ggplot(aes(x = `actupmesor`, y = `putamen_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')
```

```{r}
summary(lm(thalamus_vol_adj ~ actupmesor*Group, data = df1))
summary(lm(thalamus_vol_adj ~ actupmesor + Group, data = df1))

```
```{r}
df1 %>%
  drop_na(Group) %>%
  filter(RA > 0.4) %>%
  ggplot(aes(x = `RA`, y = `hc_vol_adj`, group = `Group`, color = `Group`))  +
  geom_point() +
  geom_smooth(method = 'lm') +
  scale_color_brewer(palette='Set1')
```
```{r}
summary(lm(hc_vol_adj ~ RA*Group, data = df1))
summary(lm(hc_vol_adj ~ RA*Group, data = filter(df1, RA > 0.4)))
summary(lm(hc_vol_adj ~ RA + age, data = filter(df1, Group == 'Older Adults')))
summary(lm(hc_vol_adj ~ RA + age, data = filter(df1, Group == 'Young Adults')))

```

## Cross-validation

```{r}
lmdf <- df1 %>%
  drop_na(hc_vol_adj, RA, Group)

beset_lm(hc_vol_adj ~ RA*Group, data = lmdf, n_folds = sum(complete.cases(lmdf)-1))
```

```{r}
lmdf <- df1 %>%
  drop_na(hc_vol_adj, actupmesor, Group)

beset_lm(hc_vol_adj ~ actupmesor * Group, data = lmdf, n_folds = sum(complete.cases(lmdf)-1))

```

## Correlation plots

```{r}
library(corrplot)

cordf <- select(df1, hc_vol_adj, IS:RA, actamp, actupmesor, fact)
cordf1 <- dplyr::mutate_all(cordf, function(x) as.numeric(as.character(x))) 
cordf1 <- cordf1[complete.cases(cordf1),]

cordft <- cor(cordf, use = 'all.obs')
corrplot(cordft)

```

```{r}
cordf <- df1 %>%
  filter(Group == 'Older Adults') %>%
  select(hc_vol_adj, IS:RA, actamp, actupmesor, fact)

cordf1 <- dplyr::mutate_all(cordf, function(x) as.numeric(as.character(x))) 
cordf1 <- cordf1[complete.cases(cordf1),]

cordft <- cor(cordf, use = 'complete.obs')
corrplot(cordft)
```

```{r}
cordf <- df1 %>%
  filter(Group == 'Young Adults') %>%
  select(hc_vol_adj, IS:RA, actamp, actupmesor, fact)

cordf1 <- dplyr::mutate_all(cordf, function(x) as.numeric(as.character(x))) 
cordf1 <- cordf1[complete.cases(cordf1),]

cordft <- cor(cordf, use = 'complete.obs')
corrplot(cordft)
```

```{r}
library(corrr)

fsvol %>% 
  merge(select(df, record_id, cvlt_zscore, cvlt_ldelay_recall, cvlt_sdelay_recall, cvlt_listb, cvlt_recognition_hits, cvlt_recognition_fp), by='record_id') %>%
  select(-record_id, -`Measure:volume`) %>% 
  corrr::correlate() %>%
  focus(cvlt_zscore, cvlt_ldelay_recall, cvlt_sdelay_recall, cvlt_listb, cvlt_recognition_hits, cvlt_recognition_fp) %>%
  arrange(desc(cvlt_ldelay_recall))

```


```{r}
df1$sex
```

