---
title: "Modularity, CR, and Aging"
author: "Megan McMahon"
date: "10/4/2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(reshape2)
library(magrittr)
library(broom)
library(knitr)
library(RColorBrewer)
library(ggcorrplot)
library(car)
```

**Main** 

[Age Effect] - Whole brain modularity changes with age

[Young Adults] - Whole brain modularity increases with age, and no significant relationship with interdaily stability, intradaily stability, or relative amplitude

[Older Adults] - whole brain modularity decreases with age, but is better explained by relative amplitude (lower relative amplitude is related to decreased modularity)

[Group Differences) - Age group differences in modularity not statistically significant

[3] No effect of IS or IV on modularity

[4](Cognition) No significant relationship between modularity and cognitive measures

```{r load data, include=FALSE}
library(readr)

rpx <- read_csv("~/Box/CogNeuroLab/Aging Decision Making R01/Data/Actigraphy/Combined Export File.csv")

efficiency <- aggregate(efficiency ~ subject_id, rpx, mean, na.action = na.omit)
sleep_time <- aggregate(sleep_time ~ subject_id, rpx, mean, na.action = na.omit)
percent_wake <- aggregate(percent_wake ~ subject_id, rpx, mean, na.action = na.omit)
onset_latency <- aggregate(onset_latency ~ subject_id, rpx, mean, na.action = na.omit)
total_ac <- aggregate(total_ac ~ subject_id, rpx, mean, na.action = na.omit)

rpx2 <- merge(efficiency, sleep_time, by = 'subject_id')
rpx2 <- merge(rpx2, percent_wake, by = 'subject_id')
rpx2 <- merge(rpx2, onset_latency, by = 'subject_id')
rpx2 <- merge(rpx2, total_ac, by = 'subject_id')
head(rpx2)

cr <- read_csv('~/Box/CogNeuroLab/Aging Decision Making R01/Data/CR/circadian_rhythms_2019-09-07.csv')
cr$actquot <- cr$actamp/cr$actmesor

neuro <- read_csv('~/Box/CogNeuroLab/Aging Decision Making R01/Data/Neuropsych/AgingDecMemNeuropsyc_DATA_2019-06-12_0708.csv')

bct <- read_csv('~/Box/CogNeuroLab/Aging Decision Making R01/Analysis/bct/bct_x.csv')

d <- merge(cr, neuro, by='record_id', all=TRUE)
d <- merge(d, bct, by='record_id', all=TRUE)
d <- merge(d, rpx2, by.x = 'record_id', by.y = 'subject_id', all=TRUE)
d <- d[(d$age >= 18) & (d$age <= 90) & !is.na(d$age), ]

d$group <- factor(ifelse(d$record_id < 40000, 0, 1), labels = c('Young Adults', 'Older Adults'))

```





## Group Differences

* No significant age group difference in whole brain modularity
```{r group differences}
t.test(wb_modularity_x ~ group, data = d)

ggplot(data = d) + 
  geom_boxplot(aes(x = group, y = wb_modularity_x, group = group, color = group), size=1.5, show.legend = FALSE) + 
  theme_minimal() +
  scale_color_manual(values = brewer.pal(8, "Paired")[7:8]) + 
  xlab('Age Group') + ylab('WB Modularity') 

```

## Age Effect

* Whole brain modularity increases with age among young adults, but decrease with age among older adults

```{r age effect}
ggplot(data = d) + 
  ggtitle('Modularity and Aging') + 
  geom_point(aes(x = age, y = wb_modularity_x, group = group, color = group), size=2, show.legend = FALSE) + 
  facet_wrap(. ~ group, scales = 'free_x', labeller = label_value) + 
  stat_smooth(aes(x = age, y = wb_modularity_x, group = group, color = group), method = 'lm', formula = y ~ x, se = TRUE, fullrange = FALSE, show.legend = FALSE) +
  theme_minimal() +
  scale_color_manual(values = brewer.pal(8, "Paired")[7:8]) + 
  xlab('Age') + ylab('WB Modularity') 
```




## Young Adults

Whole brain modularity increases with age, and no significant relationship with interdaily stability, intradaily stability, or relative amplitude

```{r young adults}

lm1 <- lm(wb_modularity_x ~ age , data = d[d$group == 'Young Adults',]) 
summary(lm1) # * .0247
lm2 <- lm(wb_modularity_x ~ age + RA , data = d[d$group == 'Young Adults',]) 
summary(lm2) # NS
lm2 <- lm(wb_modularity_x ~ age + IS , data = d[d$group == 'Young Adults',]) 
summary(lm2) # NS
lm2 <- lm(wb_modularity_x ~ age + IV , data = d[d$group == 'Young Adults',]) 
summary(lm2) # NS

lm2 <- lm(wb_modularity_x ~ group * RA , data = d)
summary(lm2) # NS

outlierTest(lm1)
durbinWatsonTest(lm1)
plot(acf(lm1$residuals))
shapiro.test(lm1$residuals) # p = 0.1406
plot(lm1)

```

## Older Adults

Older adults - decrease in whole brain modularity related to age, but better explained by relative amplitude, where lower relative amplitude is related to decreased modularity

```{r}
ggplot(data = d) + 
  ggtitle('Relative Amplitude vs. Modularity') + 
  geom_point(aes(x = RA, y = wb_modularity_x, group = group, color = group), size=2) + 
  stat_smooth(aes(x = RA, y = wb_modularity_x, group = group, color = group), method = 'lm', formula = y ~ x, se = TRUE, fullrange = FALSE) +
  theme_minimal() +
  scale_color_manual(values = brewer.pal(8, "Paired")[7:8]) + 
  xlab('Relative Amplitude') + ylab('WB Modularity') 
```


```{r older adults}
lm21 <- lm(wb_modularity_x ~ age, data = d[d$group == 'Older Adults',]) 
summary(lm21) # * .0423
AIC(lm21)
lm22 <- lm(wb_modularity_x ~ RA, data = d[d$group == 'Older Adults',]) 
summary(lm22) # * .020533
AIC(lm22)
lm23 <- lm(wb_modularity_x ~ age*RA, data = d[d$group == 'Older Adults',]) 
summary(lm23) # NS
AIC(lm23)
lm24 <- lm(wb_modularity_x ~ age + RA, data = d[d$group == 'Older Adults',]) 
summary(lm24) #only RA significant
AIC(lm24) #lm22 is best model

lm2 <- lm(wb_modularity_x ~ age + IS, data = d[d$group == 'Older Adults',]) 
summary(lm2) #NS
lm2 <- lm(wb_modularity_x ~ age + IV, data = d[d$group == 'Older Adults',]) 
summary(lm2) #NS

outlierTest(lm22) # one outlier
durbinWatsonTest(lm22) 
plot(acf(lm22$residuals)) 
plot(lm22)
```


## Cognition

As far as I can tell, these correlations do not reach statistical significance.

```{r cognition}
library(corrr)

cor_data <- select(d, RA, wb_modularity_x, cvlt_b_zscore:trails_b_z_score)

cor_data <- data.frame(apply(cor_data, 2, function(x) as.numeric(as.character(x))))

focus_out <- cor_data %>%
  correlate() %>%
  focus(wb_modularity_x)
focus_out[abs(focus_out[,2]) > 0.20,]
```

